### 2023-06-16 (2023) Fraga et al.tex
updating paper

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[preprint,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

\title{Multiproduct Batch Processing Time Maximization Problem}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author{Tatiana Balbi Fraga, Regilda Menezes and Marcos Henrique}

\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
             city={Caruaru},
             postcode={55014-900},
             state={PE},
             country={Brasil}}

%\affiliation{organization={},%Department and Organization
%            addressline={}, 
 %           city={},
 %           postcode={}, 
 %           state={},
 %          country={}}

\begin{abstract}
%% Text of abstract

\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{}
\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-harv} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem[Author(year)]{label}
%% Text of bibliographic item

\bibitem[ ()]{}

\end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2023-06-16 (2023) Fraga et al.tex
updating paper
problem definition and mathematical model

@@
 \begin{keyword}
+multiproduct batch \sep processing time maximization
 %% keywords here, in the form: keyword \sep keyword
@@
 %% main text
-\section{}
+\section{Introduction}
+\label{}
+
+\section{Multiproduct batch processing time maximization problem}
+\label{}
+
+The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in the same production batch.
+In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different production rate (quantity/unit of time) for each product.
+In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
+The maximum production quantity of each product is defined according to the demand for the product.
+However, it is still possible to stock the products and/or send them to the outlets.
+In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
+Also, there is a time limit available for processing the batch.
+The problem consists of defining the maximum processing time for the batch, respecting the limitations related to the quantities produced.
+For a better understanding of the problem, an example is presented below.
+
+\emph{Example:} A certain machine must process a batch containing 2 different products: A and B.
+The production rate of A is 60 g/min while the production rate of B is 40 g/min.
+The factory has free stock for a maximum of 3000 g of any product, and, according to the maximum stock allowed for each product, an additional 3000 g of product A and 2000 g of product B may be stocked at the factory.
+There is a demand for 1000 g of product A and 500 g of product B.
+The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.
+A maximum time of 300 minutes of this machine can be allocated for processing this batch.
+What is the maximum possible time for processing this batch ?
+
+\section{Mathematical model}
+\label{}
+
+Given that: \\
+
+$\textrm{UD}_i$ is the demand for the product $i$; \\
+
+$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch; \\
+
+$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory; \\
+
+$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets; \\
+
+$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets; \\
+
+$\textrm{p}_i$ is the production rate of product $i$; \\
+
+$\textrm{Z}$ is the timeout for batch processing; \\
+
+$P_i$ is the amount of product $i$ produced; \\
+
+$D_i$ is the amount of product $i$ delivered for the demand; \\
+
+$O_i$ amount of product $i$ shipped to factory outlets; \\
+
+$I_i$ is the amount of product $i$ that will be stored at the factory; \\
+
+$T$ is the batch processing time.
+
+We have the problem: \\
+
+\begin{equation}
+max \quad T
+\end{equation}
+
+$s.t.$ \\
+
+\begin{equation}
+P_i - \textrm{p}_i * T  = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+P_i - D_i - O_i - I_i = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_i \leq \textrm{UD}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+O_i \leq \textrm{UO}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+\sum_i{O_i} \leq \textrm{O}
+\end{equation}
+
+\begin{equation}
+I_i \leq \textrm{UI}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+\sum_i{I_i} \leq \textrm{I}
+\end{equation}
+
+\begin{equation}
+T \leq \textrm{Z}
+\end{equation}
+
+\begin{equation}
+D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
+\end{equation}
+
+where: \\
+
+Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
+Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
+Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits.
+Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stored in the factory must be less than their respective maximum allowed values.
+The restriction in (9) establishes that there is a batch processing time limit, $Z$, that must be respected.
+And finally, the constraints in (10) inform the nature of the decision variables.
+
+\section{Analytical solution}
+\label{}
+
+It is possible to consider the factory stock and the outlets stock as single stock, so we have:
+
+\begin{equation}
+E_i = O_i + I_i
+\end{equation}
+
+where $E_i$ is the sum of the quantity stored at the factory and the quantity sent to the outlets of the product $i$. \\
+
+So that:
+
+\begin{equation}
+E_i \leq \textrm{UO}_i + \textrm{UI}_i
+\end{equation}
+
+and
+
+\begin{equation}
+\sum_i {E_i} \leq \textrm{O} + \textrm{I}
+\end{equation}
+
+It is also possible to split the batch processing time into two time slots:
+
+\begin{equation}
+T = T' + T''
+\end{equation}
+
+and consider that T' is the maximum processing time used only for production that will meet the demand. Thus, we can find T', solving the reduced problem:
+
+\begin{equation}
+max \quad T'
+\end{equation}
+
+$s.t.$ \\
+
+\begin{equation}
+D_i - \textrm{p}_i * T'  = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_i \leq \textrm{UD}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_i \in  \mathbb{Z}^+ \quad \forall i
+\end{equation}
+
+\section{Tests and results}
 \label{}

### 2023-06-16 (2023) Fraga et al.tex
updating paper
analytical solution

@@
 
+This reduced problem can be rewritten in the form:
+
+\begin{equation}
+max \quad T'
+\end{equation}
+
+$s.t.$ \\
+
+\begin{equation}
+T'  \leq \textrm{UD}_i / \textrm{p}_i \quad \forall i
+\end{equation}
+
+So we have that $T'$ will be the smallest of the ratios $\textrm{UD}_i / \textrm{p}_i$ of all products. \\
+
+Once we find the value of $T'$, we can calculate the value of unmet demand for each product after $T'$, $S_i$, through the equations in (22).
+
+\begin{equation}
+S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
+\end{equation}
+
+Now we consider that the time interval $T''$ will be used for the production of the quantities that will be stored (in the factory and in the outlets), as well as of the demand not met by the production in the first time interval, $S_i$.
+
+In this case, we can find $T'''$ by solving the second reduced problem:
+
+\begin{equation}
+max \quad T''
+\end{equation}
+
+$s.t.$ \\
+
+\begin{equation}
+E_i - \textrm{p}_i * T''  = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+E_i - S_i \leq \textrm{UO}_i + \textrm{UI}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+\sum_i {E_i - S_i} \leq \textrm{O} + \textrm{I}
+\end{equation}
+
+\begin{equation}
+E_i \in  \mathbb{Z}^+ \quad \forall i
+\end{equation}
+
+Again, using a little algebra, we can rewrite this reduced problem in the form:
+
+\begin{equation}
+max \quad T''
+\end{equation}
+
+$s.t.$ \\
+
+\begin{equation}
+T'' \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i  \quad \forall i
+\end{equation}
+
+\begin{equation}
+T'' \leq (\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}
+\end{equation}
+
+So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.
+
 \section{Tests and results}

### 2023-06-17 (2023) Fraga et al.tex
updating paper
solving method :)
updating paper
including solution of exemple presented in section 2

@@
 \section{Multiproduct batch processing time maximization problem}
-\label{}
+\label{sec:MBPTMP}
 
@@
 
-$T$ is the batch processing time.
+$T$ is the batch processing time. \\
 
@@
 So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.
+\\
+
+So the solution method can be decomposed into 4 steps: \\
+
+step 1: find $T'$, where:
+
+\begin{equation}
+T' = \min {\textrm{UD}_i / \textrm{p}_i}
+\end{equation}
+
+step 2: calculate $S_i$ for all products. \\
+
+step 3: find $T''$, where:
+
+\begin{equation}
+T'' = \min \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i, (\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
+\end{equation}
+
+step 4: calculate $T$, where:
+
+\begin{equation}
+T = T' + T''
+\end{equation}
+
+\begin{equation}
+T = \min {T , Z}
+\end{equation}
+
+It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper. \\
+
+\emph{Solution for the example presented before} \\
+
+Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\
+
+$T' \leq 1000g / 60g/min$ \\
+
+$T' \leq 16,67 min$ \quad for A \\
+
+$T' \leq 500g / 40g/min$ \\
+
+$T' \leq 12,50 min$ \quad for B \\
+
+so: \\
+
+$T' = 12$ \\
+
+Then:\\
+
+$S_A = 1000g - 12min * 60g/min = 280g$ \\
+
+$S_B = 500g - 12min * 40g/min = 20g$ \\
+
+And so we have: \\
+
+$T'' \leq (3000g + 600g + 280g) / 60g/min$ \\
+
+$T'' \leq 64,67 min$ \quad for A \\
+
+$T'' \leq (2000g + 600g + 20g) / 40g/min$ \\
+
+$T'' \leq 65,50 min$ \quad for B \\
+
+$T'' \leq (1000g + 3000g + 300g) / 100g/min$ \\
+
+$T'' \leq 43 min$ \quad for A and B \\
+
+So that: \\
+
+$T'' = 43 min$ \\
+
+So we have: \\
+
+$ T = 55 min$ \\
+
+As $T<\textrm{Z}$, then this will certainly be the optimal solution. \\
+
+In this case we will have: \\
+
+$P_A = 3300g$ e $P_B=2200g$ \\
+
+$D_A = 1000g$ e $D_B = 500g$ \\
+
+$E_A = 2300g$ e $E_B = 1700g$ \\
+
+Note that it is not important to know the values of $O_i$ and $I_i$ however these values can be found by solving the indeterminate system of equations:
+
+\begin{equation}
+\sum_i{O_i} \leq \textrm{O}
+\end{equation}
+
+\begin{equation}
+\sum_i{I_i} \leq \textrm{I}
+\end{equation}
 

### 2023-06-17 (2023) Fraga et al.tex
updating paper
correction in min math function presentation

@@
 \begin{equation}
-T' = \min {\textrm{UD}_i / \textrm{p}_i}
+T' = \min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}
 \end{equation}
@@
 \begin{equation}
-T'' = \min \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i, (\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
+T'' = \min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
 \end{equation}
@@
 \begin{equation}
-T = \min {T , Z}
+T = \min \{T , Z\}
 \end{equation}
@@
 
-Note that it is not important to know the values of $O_i$ and $I_i$ however these values can be found by solving the indeterminate system of equations:
+Note that it is not important to know the values of $O_i$ and $I_i$ $\forall i$ however these values can be found by taking a solution from the indeterminate system of inequations:
 

### 2023-06-17 (2023) Fraga et al.tex
updating paper
including benchmarks

@@
 
+To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com).
+We tested the solvers developed for the benchmarks presented below.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}[c]{c r r r}
+$i$ & 1 & 2 & total \\
+\cline {1-4} \\
+$\textrm{p}_i$ & 60 & 40 & \\
+$\textrm{UD}_i$ & 1000 & 500 & \\
+$\textrm{UO}_i$ & 600 & 600 & 1000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
+\cline {1-4} \\
+& & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\label{tab:MBPTMP 001}
+\caption{Benchmark MBPTMP 001}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}[c]{c r r r r}
+$i$ & 1 & 2 & 3 & total \\
+\cline {1-5} \\
+$\textrm{p}_i$ & 60 & 40 & 50 \\
+$\textrm{UD}_i$ & 1000 & 500 & 800 \\
+$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
+\cline {1-5} \\
+& & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\label{tab:MBPTMP 001}
+\caption{Benchmark MBPTMP 002}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{c r r r r r r r r r r r }
+$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
+\cline {1-12} \\
+$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
+$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
+$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
+\cline {1-12} \\
+& & & & & & & & & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\label{tab:MBPTMP 001}
+\caption{Benchmark MBPTMP 003}
+\end{small}
+\end{center}
+\end{table}
+
+Table X presents a comparison of the results obtained by applying the analytical method and the LINGO solver for the solution of the previously presented benchmarks.
+
 %% The Appendices part is started with the command \appendix;

### 2023-06-17 (2023) Fraga et al.tex
updating paper
including benchmarks and a benchmark generation function

@@
 The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.
-A maximum time of 300 minutes of this machine can be allocated for processing this batch.
+A maximum time of 100 minutes of this machine can be allocated for processing this batch.
 What is the maximum possible time for processing this batch ?
@@
 
-As $T<\textrm{Z}$, then this will certainly be the optimal solution. \\
+As $T<\textrm{Z=100}$, then this will certainly be the optimal solution. \\
 
@@
 
+For building larger benchmarks, we used the following functions: \\
+
+\begin{equation}
+\textrm{p}_i = rand()\%30 + 10
+\end{equation}
+
+\begin{equation}
+\textrm{UD}_i = rand()\%3000 + 800;
+\end{equation}
+
+\begin{equation}
+\textrm{O} = rand()\%3000 + 500;
+\end{equation}
+
+\begin{equation}
+\textrm{UO}_i = rand()\%(\textrm{O}-500) + 500;
+\end{equation}
+
+\begin{equation}
+\textrm{I} = rand()\%5000 + 1000;
+\end{equation}
+
+\begin{equation}
+\textrm{UI}_i = rand()\%(\textrm{I}-1000) + 1000;
+\end{equation}
+
+\begin{equation}
+\textrm{Z} = 100;
+\end{equation}
+
+Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
+To build the results presented in this work, we used source=0.
+\\
+
 Table X presents a comparison of the results obtained by applying the analytical method and the LINGO solver for the solution of the previously presented benchmarks.

### 2023-06-26 (2023) Fraga et al.tex
updating paper
writing introduction section

@@
 \section{Introduction}
-\label{}
+\label{sec:intro}
+
+The literature presents several scientific papers that address the multi-product batch problem.
+Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the ideal batch size for each product, in a production of several products, which share the same production facilities and for which demand is known \citep{Eilon1985}.
+In this work, we are concerned with determining the ideal processing time for a batch consisting of a set of products, each product being or not different from the other products of the same batch.
+That is, we consider a specific case where different products are processed simultaneously on the same processor.
+This case occurs, for example, during the processing of plastic bags in extruders.
+In this process, the resins are melted, then the molten resin passes through a cylinder forming a balloon and this balloon, after cooling, will be stored in a coil.
+This coil, in turn, will be cut into several coils, forming different models of plastic bags.
 
@@
 
+\section{Contributions}
+
+The work for the elaboration of this paper is being carried out by three professors, as described below.
+Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for the analytical solution, developing benchmarks, and testing the analytical method and the solver in C++, as well as surveying bibliography and elaboration of the paper.
+Professor Henrique, M.
+is developing a solver in LINGO for testing and validating the model.
+Professor Menezes, R.
+is contributing to the bibliographic survey and to writing the bibliographic review presented in the paper.
+
 %% The Appendices part is started with the command \appendix;
@@
 
-\begin{thebibliography}{00}
+\begin{thebibliography}{1}
 
@@
 
-\bibitem[ ()]{}
+\bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
+Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt. Sci.}, Vol. 13 (5), pp. 453--468.
 

### 2023-06-26 (2023) Fraga et al.tex
updating paper
writing introduction section - before Regi contribution.

@@
 
-\journal{Nuclear Physics B}
+\journal{Journal of Analysis, Modeling and Optimization}
 
@@
 
-The literature presents several scientific papers that address the multi-product batch problem.
-Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the ideal batch size for each product, in a production of several products, which share the same production facilities and for which demand is known \citep{Eilon1985}.
+The scientific literature presents several papers that address the multi-product batch problem.
+Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products, which share the same production facilities and for which demand is known \citep{Eilon1985}.
+In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed.
+Ordering is often also important due to high setup costs.
+
 In this work, we are concerned with determining the ideal processing time for a batch consisting of a set of products, each product being or not different from the other products of the same batch.
 That is, we consider a specific case where different products are processed simultaneously on the same processor.
-This case occurs, for example, during the processing of plastic bags in extruders.
-In this process, the resins are melted, then the molten resin passes through a cylinder forming a balloon and this balloon, after cooling, will be stored in a coil.
-This coil, in turn, will be cut into several coils, forming different models of plastic bags.
+This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, and after cooling, is stored in a coil which, in turn, is cut into several smaller coils, forming different models of plastic bags.
 

### 2023-06-26 (2023) Fraga et al.tex
updating paper
writing intruduction - before Regi contribuction

@@
 \begin{keyword}
-multiproduct batch \sep processing time maximization
+multiproduct batch \sep processing time maximization \sep anal
 %% keywords here, in the form: keyword \sep keyword
@@
 The scientific literature presents several papers that address the multi-product batch problem.
-Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products, which share the same production facilities and for which demand is known \citep{Eilon1985}.
+Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
 In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed.
-Ordering is often also important due to high setup costs.
+The solution must be determined in such a way that both setup and storage costs are minimized.
+Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
+Other important works deal with the design of a multi-product batch plant.
+In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the
+equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
 
@@
 \bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
-Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt. Sci.}, Vol. 13 (5), pp. 453--468.
+Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt Sci.}, Vol. 13 (5), pp. 453--468.
+
+\bibitem[\protect\citeauthoryear{Liu et al}{2020}]{LiuEtAl2020}
+Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.
+
+\bibitem[\protect\citeauthoryear{Omega}{1993}]{Omega1993}
+OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.
+
+\bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}
+Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.
 

### 2023-06-26 (2023) Fraga et al.tex
updating paper
writing introduction - before Regi's contribution

@@
 The scientific literature presents several papers that address the multi-product batch problem.
-Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
+Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
 In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed.
@@
 Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
+In the papers mentioned above, production in a single unit or in a  simple serial flowshop plant is considered, in which all products follow the same linear flow through the production units.
+\cite{KimEtAl1996} consider the multi-product batch problem in networked processes.
+As defined by the authors, in this case, the production units are not arranged in a line, and the connection between the units may or may not exist.
+Therefore, the production paths in the flowshop network can be different for each product.
+Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence.
 Other important works deal with the design of a multi-product batch plant.
-In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the
-equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
+In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
 
@@
 This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, and after cooling, is stored in a coil which, in turn, is cut into several smaller coils, forming different models of plastic bags.
+
+In the next sections, a presentation of the multi-product batch processing time maximization problem is made, along with an application example.
+Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
+Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
+In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions of this work are informed and acknowledgments are given, respectively.
+Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
 
@@
 \section{Mathematical model}
-\label{}
+\label{sec:mathModel}
 
@@
 \section{Analytical solution}
-\label{}
+\label{sec:analyticalSol}
 
@@
 \section{Tests and results}
-\label{}
+\label{sec:results}
 
@@
 \section{Contributions}
+\label{sec:contributions}
 
@@
 is contributing to the bibliographic survey and to writing the bibliographic review presented in the paper.
+
+\section{Acknowledgments}
+\label{sec:acknowledgments}
+
+\section{Conclusions and suggestions for future works}
+\label{sec:conclusions}
 
@@
 
-\bibitem[\protect\citeauthoryear{Liu et al}{2020}]{LiuEtAl2020}
+\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
+Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.
+
+\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
 Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.
 
-\bibitem[\protect\citeauthoryear{Omega}{1993}]{Omega1993}
+\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
 OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.

### 2023-06-26 (2023) Fraga et al.tex
updating paper

@@
 \begin{keyword}
-multiproduct batch \sep processing time maximization \sep anal
+multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
 %% keywords here, in the form: keyword \sep keyword
@@
 Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence.
-Other important works deal with the design of a multi-product batch plant.
+Other important works deal with the problem of a multi-product batch plant design (MPBPD).
 In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
@@
 
-In the next sections, a presentation of the multi-product batch processing time maximization problem is made, along with an application example.
+As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and an analytical solution method for solving this problem.
+
+In the next sections, a presentation of problem is made along with an application example.
 Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
@@
 
+We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
+We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
+Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professor Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
+
 \section{Conclusions and suggestions for future works}

### 2023-06-26 (2023) Fraga et al.tex
updating paper
small corrections

@@
 That is, we consider a specific case where different products are processed simultaneously on the same processor.
-This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, and after cooling, is stored in a coil which, in turn, is cut into several smaller coils, forming different models of plastic bags.
+This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils, forming different models of plastic bags.
 

### 2023-06-26 (2023) Fraga et al.tex
updating paper

@@
 
-\author{Tatiana Balbi Fraga, Regilda Menezes and Marcos Henrique}
+\author{Tatiana Balbi Fraga, Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique}
 
@@
 
-The scientific literature presents several papers that address the multi-product batch problem.
+The scientific literature presents several papers that address multi-product batch problens.
 Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
@@
 Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stored in the factory must be less than their respective maximum allowed values.
-The restriction in (9) establishes that there is a batch processing time limit, $Z$, that must be respected.
+The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
 And finally, the constraints in (10) inform the nature of the decision variables.
@@
 
-and consider that T' is the maximum processing time used only for production that will meet the demand. Thus, we can find T', solving the reduced problem:
+and consider that $T'$ is the maximum processing time used only for production that will meet the demand. Thus, we can find $T'$, solving the reduced problem:
 
@@
 \begin{equation}
-T'  \leq \textrm{UD}_i / \textrm{p}_i \quad \forall i
+T'  \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
 \end{equation}
 
-So we have that $T'$ will be the smallest of the ratios $\textrm{UD}_i / \textrm{p}_i$ of all products. \\
+So we have that $T'$ will be the smallest of the ratios $\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor$ of all products. \\
 
-Once we find the value of $T'$, we can calculate the value of unmet demand for each product after $T'$, $S_i$, through the equations in (22).
+Once we find the value of $T'$, we can calculate the value of unmet demand for each product after $T'$, $S_i$, through the equations in (\ref{eq:unmet1}).
 
 \begin{equation}
+\label{eq:unmet1}
 S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
@@
 \begin{equation}
-T'' \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i  \quad \forall i
+T'' \leq \lfloor{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i}\rfloor  \quad \forall i
 \end{equation}
@@
 \begin{equation}
-T'' \leq (\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}
+T'' \leq \lfloor{(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}}\rfloor
 \end{equation}
@@
 \begin{equation}
-T' = \min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}
+T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
 \end{equation}
 
-step 2: calculate $S_i$ for all products. \\
+step 2: calculate $S_i$ for all products.
+
+\begin{equation}
+\label{eq:unmet}
+S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
+\end{equation}
 
@@
 \begin{equation}
-T'' = \min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}
+T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
 \end{equation}
@@
 Professor Henrique, M.
+L.
 is developing a solver in LINGO for testing and validating the model.
 Professor Menezes, R.
+D.
+C.
+S.
 is contributing to the bibliographic survey and to writing the bibliographic review presented in the paper.

### 2023-06-26 (2023) Fraga et al.tex
updating paper

@@
 
-\author{Tatiana Balbi Fraga, Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique}
+\author{Tatiana Balbi Fraga and Regilda da Costa e Silva Menêzes}
 
@@
 
-The work for the elaboration of this paper is being carried out by three professors, as described below.
+The work for the elaboration of this paper is being carried out by two professors, as described below.
 Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for the analytical solution, developing benchmarks, and testing the analytical method and the solver in C++, as well as surveying bibliography and elaboration of the paper.
-Professor Henrique, M.
-L.
-is developing a solver in LINGO for testing and validating the model.
 Professor Menezes, R.

### 2023-06-27 (2023) Fraga et al.tex
updating paper

@@
 The scientific literature presents several papers that address multi-product batch problens.
-Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
+Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
 In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed.
@@
 \begin{equation}
-D_i \in  \mathbb{Z}^+ \quad \forall i
+D_i, T' \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
@@
 \begin{equation}
-E_i \in  \mathbb{Z}^+ \quad \forall i
+E_i, T'' \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
@@
 \begin{equation}
-T = \min \{T , Z\}
+T = \min \{T , \textrm{Z}\}
 \end{equation}
@@
 
-$T' \leq 1000g / 60g/min$ \\
+$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T' \leq 16,67 min$ \quad for A \\
+$T' \leq 16 \textrm{ min}$ \quad for A \\
 
-$T' \leq 500g / 40g/min$ \\
+$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T' \leq 12,50 min$ \quad for B \\
+$T' \leq 12 \textrm{ min}$ \quad for B \\
 
@@
 
-$T' = 12$ \\
+$T' = 12 \textrm{ min}$ \\
 
@@
 
-$S_A = 1000g - 12min * 60g/min = 280g$ \\
+$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$ \\
 
-$S_B = 500g - 12min * 40g/min = 20g$ \\
+$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$ \\
 
@@
 
-$T'' \leq (3000g + 600g + 280g) / 60g/min$ \\
+$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T'' \leq 64,67 min$ \quad for A \\
+$T'' \leq 64 \textrm{ min}$ \quad for A \\
 
-$T'' \leq (2000g + 600g + 20g) / 40g/min$ \\
+$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T'' \leq 65,50 min$ \quad for B \\
+$T'' \leq 65 \textrm{ min}$ \quad for B \\
 
-$T'' \leq (1000g + 3000g + 300g) / 100g/min$ \\
+$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T'' \leq 43 min$ \quad for A and B \\
+$T'' \leq 43 \textrm{ min}$ \quad for A and B \\
 
@@
 
-$T'' = 43 min$ \\
+$T'' = 43 \textrm{ min}$ \\
 
@@
 
-$ T = 55 min$ \\
+$T = 55 \textrm{ min}$ \\
 
-As $T<\textrm{Z=100}$, then this will certainly be the optimal solution. \\
+As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution. \\
 
@@
 
-$P_A = 3300g$ e $P_B=2200g$ \\
+$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$ \\
 
-$D_A = 1000g$ e $D_B = 500g$ \\
+$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$ \\
 
-$E_A = 2300g$ e $E_B = 1700g$ \\
+$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$ \\
 
@@
 \begin{equation}
-\textrm{p}_i = rand()\%30 + 10
+\textrm{p}_i = \textrm{rand}()\%30 + 10
 \end{equation}
@@
 \begin{equation}
-\textrm{UD}_i = rand()\%3000 + 800;
+\textrm{UD}_i = \textrm{rand}()\%3000 + 800;
 \end{equation}
@@
 \begin{equation}
-\textrm{O} = rand()\%3000 + 500;
+ \textrm{seed1} = \textrm{rand}()\%3000 + 500;
 \end{equation}
@@
 \begin{equation}
-\textrm{UO}_i = rand()\%(\textrm{O}-500) + 500;
+\textrm{seed2} = \textrm{rand}()\%5000 + 1000;
 \end{equation}
@@
 \begin{equation}
-\textrm{I} = rand()\%5000 + 1000;
+\textrm{O} = \textrm{N}/2*\textrm{seed1};
 \end{equation}
@@
 \begin{equation}
-\textrm{UI}_i = rand()\%(\textrm{I}-1000) + 1000;
+\textrm{UO}_i = \textrm{rand}()\%(\textrm{seed1}-500) + 500;
+\end{equation}
+
+\begin{equation}
+\textrm{I} = \textrm{N}/2*\textrm{seed2};
+\end{equation}
+
+\begin{equation}
+\textrm{UI}_i = \textrm{rand}()\%(\textrm{seed2}-1000) + 1000;
 \end{equation}
@@
 
+Randomly generated benchmarks were named RMBPTMP $\textrm{N}$, being $\textrm{N}$ the number of products.
+
 Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
@@
 
-Table X presents a comparison of the results obtained by applying the analytical method and the LINGO solver for the solution of the previously presented benchmarks.
+Table X presents the results obtained by applying the analytical method and the LINGO solver for the solution of the previously presented benchmarks.
+
+\begin{table}[h]
+\begin{center}
+\begin{footnotesize}
+\begin{tabular}[c]{l r r r r}
+problem & LINGO solver & time (s) & analytical method & time (s) \\
+\cline {1-5} \\
+MBPTMP 1 & & & 52 & 0 \\
+MBPTMP 2 & & & 46 & 0 \\
+MBPTMP 3 & & & 30 & 0 \\
+RMBPTMP 20 & & & 100 & 0 \\
+RMBPTMP 50 & & & 98 & 0\\
+RMBPTMP 100 & & & 98 & 0\\
+RMBPTMP 1,000 & & & 78 & 0\\
+RMBPTMP 10,000 & & & 70 & 0 \\
+\cline {1-5} \\
+\end{tabular}
+\label{tab:results}
+\caption{Results obtained with the LINGO solver and the analytical method}
+\end{footnotesize}
+\end{center}
+\end{table}
 
@@
 S.
-is contributing to the bibliographic survey and to writing the bibliographic review presented in the paper.
+is contributing to the bibliographic survey.
 

### 2023-06-27 (2023) Fraga et al.tex
updating paper

@@
 Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
-In the papers mentioned above, production in a single unit or in a  simple serial flowshop plant is considered, in which all products follow the same linear flow through the production units.
+In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow the same linear flow through the production units.
 \cite{KimEtAl1996} consider the multi-product batch problem in networked processes.
@@
 Randomly generated benchmarks were named RMBPTMP $\textrm{N}$, being $\textrm{N}$ the number of products.
-
 Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
@@
 
-Table X presents the results obtained by applying the analytical method and the LINGO solver for the solution of the previously presented benchmarks.
+Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks.
 
@@
 The work for the elaboration of this paper is being carried out by two professors, as described below.
-Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for the analytical solution, developing benchmarks, and testing the analytical method and the solver in C++, as well as surveying bibliography and elaboration of the paper.
+Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for the analytical solution and a solver in LINGO for validating the mathematical model, developing benchmarks, and testing the analytical method and the solver in C++, as well as surveying bibliography and elaboration of the paper.
 Professor Menezes, R.
@@
 We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
-Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professor Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
+Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
+We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.
 

### 2023-06-27 (2023) Fraga et al.tex
updating paper

@@
 To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com).
+The tests were performed on a notebook with an Intel i7 processor.
 We tested the solvers developed for the benchmarks presented below.
@@
 \cline {1-5} \\
-MBPTMP 1 & & & 52 & 0 \\
-MBPTMP 2 & & & 46 & 0 \\
-MBPTMP 3 & & & 30 & 0 \\
-RMBPTMP 20 & & & 100 & 0 \\
-RMBPTMP 50 & & & 98 & 0\\
-RMBPTMP 100 & & & 98 & 0\\
-RMBPTMP 1,000 & & & 78 & 0\\
-RMBPTMP 10,000 & & & 70 & 0 \\
+MBPTMP 1 & 55 & 0 & 55 & 0.001 \\
+MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
+MBPTMP 3 & & & 30 & 0.001 \\
+RMBPTMP 20 & & & 100 & 0.001 \\
+RMBPTMP 50 & & & 98 & 0.001\\
+RMBPTMP 100 & & & 98 & 0.002\\
+RMBPTMP 1,000 & & & 78 & 0.002\\
+RMBPTMP 10,000 & & & 70 & 0.006 \\
 \cline {1-5} \\

### 2023-07-03 (2023) Fraga et al.tex
updating files

@@
 
-\documentclass[preprint,12pt,authoryear]{elsarticle}
+\documentclass[review,12p]{elsarticle}
+
+%% The `ecrc' package must be called to make the CRC functionality available
+%\usepackage{ecrc}
 
@@
 \begin{graphicalabstract}
-%\includegraphics{grabs}
+\includegraphics[width=13cm]{graphical.png}
 \end{graphicalabstract}
@@
 
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+
 Given that: \\
@@
 \end{equation}
-
-$s.t.$ \\
-
+$\qquad \qquad \qquad \qquad \qquad \qquad s.t.$ \\
 \begin{equation}
@@
 \end{equation}
-
 \begin{equation}
@@
 \end{equation}
-
 \begin{equation}
-D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
+T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
@@
 
-So the solution method can be decomposed into 4 steps: \\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+a\\
+
+The analytical method can be decomposed into 4 steps: \\
 
 step 1: find $T'$, where:
-
 \begin{equation}
@@
 step 2: calculate $S_i$ for all products.
-
 \begin{equation}
@@
 step 3: find $T''$, where:
-
 \begin{equation}
@@
 step 4: calculate $T$, where: 
-
 \begin{equation}
@@
 MBPTMP 3 & & & 30 & 0.001 \\
-RMBPTMP 20 & & & 100 & 0.001 \\
-RMBPTMP 50 & & & 98 & 0.001\\
-RMBPTMP 100 & & & 98 & 0.002\\
-RMBPTMP 1,000 & & & 78 & 0.002\\
-RMBPTMP 10,000 & & & 70 & 0.006 \\
+RMBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
+RMBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
+RMBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
+RMBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
+RMBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
 \cline {1-5} \\

### 2023-07-04 (2023) Fraga et al.tex
updating paper

--- 2023-06-27 (2023) Fraga et al.tex
@@
 
-\documentclass[preprint,12pt,authoryear]{elsarticle}
+\documentclass[authoryear,preprint,12pt]{elsarticle}
+
+%% The `ecrc' package must be called to make the CRC functionality available
+%\usepackage{ecrc}
 
@@
 
-\title{Multiproduct Batch Processing Time Maximization Problem}
+\title{Multi-product Batch Processing Time Maximization Problem}
 
@@
 
-\author{Tatiana Balbi Fraga and Regilda da Costa e Silva Menêzes}
+\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}
 
@@
 
-The scientific literature presents several papers that address multi-product batch problens.
+The scientific literature presents several papers that address multi-product batch problems.
 Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
@@
 
-$\textrm{UD}_i$ is the demand for the product $i$; \\
+$\textrm{UD}_i$ is the demand for the product $i$;
 
-$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch; \\
+$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;
 
-$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory; \\
+$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;
 
-$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets; \\
+$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;
 
-$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets; \\
+$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;
 
-$\textrm{p}_i$ is the production rate of product $i$; \\
+$\textrm{p}_i$ is the production rate of product $i$;
 
-$\textrm{Z}$ is the timeout for batch processing; \\
+$\textrm{Z}$ is the timeout for batch processing;
 
-$P_i$ is the amount of product $i$ produced; \\
+$P_i$ is the amount of product $i$ produced;
 
-$D_i$ is the amount of product $i$ delivered for the demand; \\
+$D_i$ is the amount of product $i$ delivered for the demand;
 
-$O_i$ amount of product $i$ shipped to factory outlets; \\
+$O_i$ amount of product $i$ shipped to factory outlets;
 
-$I_i$ is the amount of product $i$ that will be stored at the factory; \\
+$I_i$ is the amount of product $i$ that will be stored at the factory;
 
@@
 
-$s.t.$ \\
+$s.t.$
 
@@
 \begin{equation}
-D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
+T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
@@
 
-So the solution method can be decomposed into 4 steps: \\
+So, the analytical method can be decomposed into 4 steps: \\
 
 step 1: find $T'$, where:
-
 \begin{equation}
@@
 
-Note that it is not important to know the values of $O_i$ and $I_i$ $\forall i$ however these values can be found by taking a solution from the indeterminate system of inequations:
+Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining $T$, these values can be found by taking a solution from the model:
+
+\begin{equation}
+max \quad \sum_i{D_i}
+\end{equation}
+
+$s.t.$
+
+\begin{equation}
+P_i  = \textrm{p}_i * T \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_i - O_i - I_i = P_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_i \leq \textrm{UD}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+O_i \leq \textrm{UO}_i \quad \forall i
+\end{equation}
 
@@
 \begin{equation}
+I_i \leq \textrm{UI}_i \quad \forall i
+\end{equation}
+
+\begin{equation}
 \sum_i{I_i} \leq \textrm{I}
+\end{equation}
+
+\begin{equation}
+D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
@@
 
-Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks.
+Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks. \\
 
@@
 \cline {1-5} \\
-MBPTMP 1 & 55 & 0 & 55 & 0.001 \\
+MBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
 MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
-MBPTMP 3 & & & 30 & 0.001 \\
-RMBPTMP 20 & & & 100 & 0.001 \\
-RMBPTMP 50 & & & 98 & 0.001\\
-RMBPTMP 100 & & & 98 & 0.002\\
-RMBPTMP 1,000 & & & 78 & 0.002\\
-RMBPTMP 10,000 & & & 70 & 0.006 \\
+MBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
+RMBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
+RMBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
+RMBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
+RMBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
+RMBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
 \cline {1-5} \\
@@
 
-\section{Contributions}
+It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
+As the analytical method is non-polynomial, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
+
+We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi period problem and try to propose new solution methods if needed.
+
+\section{Contributions to this work}
 \label{sec:contributions}
 
-The work for the elaboration of this paper is being carried out by two professors, as described below.
-Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for the analytical solution and a solver in LINGO for validating the mathematical model, developing benchmarks, and testing the analytical method and the solver in C++, as well as surveying bibliography and elaboration of the paper.
+The work for the elaboration of this paper was carried out by tree contributors, as described below.
+Aquino, Í.R.B., developed the detailed study on the plastic bag production process, which made it possible to identify the problem addressed in this paper.
+Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for applying the analytical solution and a solver in LINGO for validating the mathematical model and the results found by the first solver, developing benchmarks, and testing the model and analytical method proposed, as well as surveying bibliography and elaboration of the paper.
 Professor Menezes, R.
@@
 C.
-S.
-is contributing to the bibliographic survey.
+S., contributed to the bibliographic survey.
+The authorship of this work follows as described contributions.
+
+\section{Conclusions and suggestions for future works}
+\label{sec:conclusions}
+
+In this paper we presented the Multi-product Batch Processing Time Maximization Problem, as well as a mathematical model and an analytical solution method for this problem.
+The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO tool, from LINDO Systems, and with a solver developed in C++ language.
+Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
+As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem with more than one day of planning.
+We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
 
@@
 We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.
-
-\section{Conclusions and suggestions for future works}
-\label{sec:conclusions}
 

### 2023-07-04 (2023) Fraga et al.tex
updating paper

@@
 
-To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com).
+To test the developed model and analytical solution method, we created a solver in C++ (https://github.com/tbfraga/project-combinatorial-optimization-problems/tree/main/combinatorial-optimization-solver) and a solver in LINGO (https://github.com/tbfraga/project-combinatorial-optimization-problems/tree/main/lingo-solvers/MPBPTMP).
 The tests were performed on a notebook with an Intel i7 processor.
-We tested the solvers developed for the benchmarks presented below.
+We tested the solvers developed for the benchmarks presented below (and available on github https://github.com/tbfraga/project-combinatorial-optimization-problems/tree/main/lingo-solvers/MPBPTMP/benchmarcks).
 

### 2023-07-04 (2023) Fraga et al.tex
updating paper
small corrections and highlights

@@
 \begin{highlights}
-\item Research highlight 1
-\item Research highlight 2
+\item this paper presents a brief bibliographic review on multi-product batch problems;
+\item presents a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
+\item presents a linear integer programming model for the MPBPTM problem;
+\item proposes a polynomial time analytical method for solving the MPBPTM problem.
 \end{highlights}
@@
 It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is non-polynomial, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
+As the analytical method is a polynomial method, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
 

### 2023-07-05 (2023) Fraga et al.tex
updating paper

--- 2023-07-04 (2023) Fraga et al.tex
@@
 
-\journal{Journal of Analysis, Modeling and Optimization}
+\journal{Applied Mathematical Modelling}
 
@@
 \begin{abstract}
-%% Text of abstract
-
+In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates.
+The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch.
+In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem.
+We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
 \end{abstract}
@@
 Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
-In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow the same linear flow through the production units.
+\cite{MendezEtAll2000} and \cite{ShiEtAll2017} deal with a parallel multi-product batch scheduling  (PMPBS) problem, in which production units of the same type are arranged in parallel, forming each production stage.
+In this case, it is also necessary to define in which units each product will be processed.
+The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance).
+In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages.
 \cite{KimEtAl1996} consider the multi-product batch problem in networked processes.
-As defined by the authors, in this case, the production units are not arranged in a line, and the connection between the units may or may not exist.
+As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist.
 Therefore, the production paths in the flowshop network can be different for each product.
@@
 Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions of this work are informed and acknowledgments are given, respectively.
+In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions for this work are informed and acknowledgments are given, respectively.
 Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
@@
 
-The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in the same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different production rate (quantity/unit of time) for each product.
+The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
+In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different proportionality rate (prodction rate) for each product.
 In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
-The maximum production quantity of each product is defined according to the demand for the product.
+The maximum production quantity of each product is mainly defined according to the demand for the product.
 However, it is still possible to stock the products and/or send them to the outlets.
@@
 The production rate of A is 60 g/min while the production rate of B is 40 g/min.
-The factory has free stock for a maximum of 3000 g of any product, and, according to the maximum stock allowed for each product, an additional 3000 g of product A and 2000 g of product B may be stocked at the factory.
+The factory has free stock for a maximum of 3000 g of any product, and, according to the company inventory policy, an additional 3000 g of product A and 2000 g of product B may be stocked at the factory.
 There is a demand for 1000 g of product A and 500 g of product B.
@@
 
-Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining $T$, these values can be found by taking a solution from the model:
+Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the indeterminated system of inequations:
 
 \begin{equation}
-max \quad \sum_i{D_i}
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-P_i  = \textrm{p}_i * T \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i - O_i - I_i = P_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
+O_i + I_i = E_i \quad \forall i
 \end{equation}
@@
 \begin{equation}
-D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
+O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (both available at github.com).
+To test the developed model and analytical solution method, we created a solver in C++ (https://github.com/blinded) and a solver in LINGO (https://github.com/blinded).
 The tests were performed on a notebook with an Intel i7 processor.
@@
 To build the results presented in this work, we used source=0.
-\\
+The benchmarks used for the tests performed can be consulted at github.com/blinded.
 
@@
 It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is non-polynomial, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
+As the analytical method is a polynomial time complexity method, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
 
@@
 The work for the elaboration of this paper was carried out by tree contributors, as described below.
-Aquino, Í.R.B., developed the detailed study on the plastic bag production process, which made it possible to identify the problem addressed in this paper.
-Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for applying the analytical solution and a solver in LINGO for validating the mathematical model and the results found by the first solver, developing benchmarks, and testing the model and analytical method proposed, as well as surveying bibliography and elaboration of the paper.
-Professor Menezes, R.
-D.
-C.
-S., contributed to the bibliographic survey.
+Blinded, developed the detailed study on the plastic bag production process, which made it possible to identify the problem addressed in this paper.
+Blinded was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for applying the analytical solution and a solver in LINGO for validating the mathematical model and the results found by the first solver, developing benchmarks, and testing the model and analytical method proposed, as well as surveying bibliography and elaboration of the paper.
+Blinded contributed to the bibliographic survey.
 The authorship of this work follows as described contributions.
@@
 
+\bibitem[\protect\citeauthoryear{Méndez \emph{et al.}}{2000}]{MendezEtAll2000}
+Méndez, C.A., Henning, G.P., Cerdá, J. (2000). Optimal scheduling of batch plants satisfying multiple product
+orders with different due-dates. {\it Computers and Chemical Engineering}, Vol. 24, pp. 2223--2245.
+
 \bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
@@
 Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.
+
+\bibitem[\protect\citeauthoryear{Shi \emph{et al.}}{2017}]{ShiEtAll2017}
+Shi, B., Qian, X., Sun, S., Yan, L. (2017). Rule-based scheduling of multi-stage multi-product batch plants with parallel units. {\it Chinese Journal of Chemical Engineering}, in press.
 

### 2023-07-05 (2023) Fraga et al.tex
updating paper

@@
 \begin{highlights}
-\item this paper presents a brief bibliographic review on multi-product batch problems;
-\item presents a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
-\item presents a linear integer programming model for the MPBPTM problem;
-\item proposes a polynomial time analytical method for solving the MPBPTM problem.
+\item brief bibliographic review on multi-product batch problems;
+\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
+\item linear integer programming model for the MPBPTM problem;
+\item polynomial time complexity analytical method for solving the MPBPTM problem.
 \end{highlights}
@@
 Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
-\cite{MendezEtAll2000} and \cite{ShiEtAll2017} deal with a parallel multi-product batch scheduling  (PMPBS) problem, in which production units of the same type are arranged in parallel, forming each production stage.
+\cite{MendezEtAll2000} and \cite{ShiEtAll2017} present two parallel multi-product batch scheduling (PMPBS) problems, in which production units of the same type are arranged in parallel, forming each production stage.
 In this case, it is also necessary to define in which units each product will be processed.
@@
 That is, we consider a specific case where different products are processed simultaneously on the same processor.
-This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils, forming different models of plastic bags.
+This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.
 
-As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and an analytical solution method for solving this problem.
+As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution method for solving this problem.
 
@@
 Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions for this work are informed and acknowledgments are given, respectively.
+In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
 Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
@@
 The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different proportionality rate (prodction rate) for each product.
+In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (prodction rate) for each product.
 In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
@@
 
-Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the indeterminated system of inequations:
+Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the undetermined system of inequalities:
 

### 2023-07-05 (2023) Fraga et al.tex
updating paper
manuscript - final

@@
 The production rate of A is 60 g/min while the production rate of B is 40 g/min.
-The factory has free stock for a maximum of 3000 g of any product, and, according to the company inventory policy, an additional 3000 g of product A and 2000 g of product B may be stocked at the factory.
+The factory has free stock for a maximum of 3000 g of any product, and, according to the company's inventory policy, a maximum of 3000 g of product A and 2000 g of product B can be stocked at the factory.
 There is a demand for 1000 g of product A and 500 g of product B.
@@
 Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits.
-Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stored in the factory must be less than their respective maximum allowed values.
+Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
 The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
@@
 The tests were performed on a notebook with an Intel i7 processor.
-We tested the solvers developed for the benchmarks presented below.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r}
-$i$ & 1 & 2 & total \\
-\cline {1-4} \\
-$\textrm{p}_i$ & 60 & 40 & \\
-$\textrm{UD}_i$ & 1000 & 500 & \\
-$\textrm{UO}_i$ & 600 & 600 & 1000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
-\cline {1-4} \\
-& & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\label{tab:MBPTMP 001}
-\caption{Benchmark MBPTMP 001}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r r}
-$i$ & 1 & 2 & 3 & total \\
-\cline {1-5} \\
-$\textrm{p}_i$ & 60 & 40 & 50 \\
-$\textrm{UD}_i$ & 1000 & 500 & 800 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
-\cline {1-5} \\
-& & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\label{tab:MBPTMP 001}
-\caption{Benchmark MBPTMP 002}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{c r r r r r r r r r r r }
-$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
-\cline {1-12} \\
-$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
-$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
-\cline {1-12} \\
-& & & & & & & & & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\label{tab:MBPTMP 001}
-\caption{Benchmark MBPTMP 003}
-\end{small}
-\end{center}
-\end{table}
-
-For building larger benchmarks, we used the following functions: \\
+We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
 
@@
 
-Randomly generated benchmarks were named RMBPTMP $\textrm{N}$, being $\textrm{N}$ the number of products.
+\begin{table}[h]
+\begin{center}
+\begin{tabular}[c]{c r r r}
+$i$ & 1 & 2 & total \\
+\cline {1-4} \\
+$\textrm{p}_i$ & 60 & 40 & \\
+$\textrm{UD}_i$ & 1000 & 500 & \\
+$\textrm{UO}_i$ & 600 & 600 & 1000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
+\cline {1-4} \\
+& & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\caption{Benchmark MBPTMP 001}
+\label{tab:MBPTMP001}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}[c]{c r r r r}
+$i$ & 1 & 2 & 3 & total \\
+\cline {1-5} \\
+$\textrm{p}_i$ & 60 & 40 & 50 \\
+$\textrm{UD}_i$ & 1000 & 500 & 800 \\
+$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
+\cline {1-5} \\
+& & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\caption{Benchmark MBPTMP 002}
+\label{tab:MBPTMP002}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{small}
+\begin{tabular}[c]{c r r r r r r r r r r r }
+$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
+\cline {1-12} \\
+$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
+$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
+$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
+$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
+\cline {1-12} \\
+& & & & & & & & & & $\textrm{Z}$ & 100 \\
+\end{tabular}
+\caption{Benchmark MBPTMP 003}
+\label{tab:MBPTMP003}
+\end{small}
+\end{center}
+\end{table}
+
+Randomly generated benchmarks were named RMPBPTMP $\textrm{N}$, being $\textrm{N}$ the number of products.
 Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
@@
 
-Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks. \\
+Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks.
 
@@
 \end{tabular}
+\caption{Results obtained with the LINGO solver and the analytical method}
 \label{tab:results}
-\caption{Results obtained with the LINGO solver and the analytical method}
 \end{footnotesize}
@@
 It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is a polynomial time complexity method, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
+As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
 
-We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi period problem and try to propose new solution methods if needed.
+We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi-period problem and try to propose new solution methods if needed.
 
@@
 Blinded contributed to the bibliographic survey.
-The authorship of this work follows as described contributions.
+The authorship of this work is distributed according to contributions described.
 
@@
 In this paper we presented the Multi-product Batch Processing Time Maximization Problem, as well as a mathematical model and an analytical solution method for this problem.
-The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO tool, from LINDO Systems, and with a solver developed in C++ language.
+The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
 Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
-As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem with more than one day of planning.
+As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem in a multi-period scenario.
 We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
@@
 
-We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
+Blinded.
+%We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
 We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.

### 2023-07-05 (2023) Fraga et al.tex
updating files

@@
 
-\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}
+%\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}
 
-\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
-             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
-             city={Caruaru},
-             postcode={55014-900},
-             state={PE},
-             country={Brasil}}
+%\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
+%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
+%             city={Caruaru},
+%             postcode={55014-900},
+%             state={PE},
+%             country={Brasil}}
 

### 2023-07-05 cover.tex
updating files

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[
  fontsize=11pt,
  paper=a4,
  parskip=half,
  enlargefirstpage=on,    % More space on first page
  fromalign=right,        % PLacement of name in letter head
  fromphone=off,          % Turn on phone number of sender
  fromrule=aftername,     % Rule after sender name in letter head
  addrfield=on,           % Adress field for envelope with window
  backaddress=on,         % Sender address in this window
  subject=beforeopening,  % Placement of subject
  locfield=narrow,        % Additional field for sender
  foldmarks=on,           % Print foldmarks
]{scrlttr2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{blindtext}

\setkomafont{fromname}{\sffamily \LARGE}
\setkomafont{fromaddress}{\sffamily}%% statt \small
\setkomafont{pagenumber}{\sffamily}
\setkomafont{subject}{\bfseries}
\setkomafont{backaddress}{\mdseries}

\LoadLetterOption{DIN}
\setkomavar{fromname}{Tatiana Balbi Fraga}
\setkomavar{fromaddress}{Avenida Marielle Franco, Bairro Nova Caruaru, Caruaru, PE, Brazil}
\setkomavar{fromphone}{+55 (81)  9\,8947\,9100}
\setkomavar{fromemail}{tatiana.balbi@ufpe.br}
\setkomavar{backaddressseparator}{\enspace\textperiodcentered\enspace}
\setkomavar{signature}{Tatiana Balbi Fraga \\ 
Founding leader of the Systems Analysis, Modeling and Optimization Group \\
and Professor of the Production Engineering Course \\
at the Academic Center of Agreste - Federal University of Pernambuco}
\setkomavar{place}{Caruaru}
\setkomavar{date}{\today}
\setkomavar{enclseparator}{: }

\begin{document}

\begin{letter}{To Applied Mathematical Modelling journal}
    \setkomavar{subject}{Cover letter}
    \opening{Dear editor,}

	Along with this letter, I am sending a paper in which I present the Multi-product Batch Processing Time Maximization (MPBPTM) problem, as well as a mathematical model and an analytical solution method with polynomial time complexity.

The problem was identified by me during the development of a solver for production planning in extruders.

As I am applying a local search heuristic, at each iteration I need to generate a new solution, and therefore I need to solve the MPBPTM problem.

I had a vague idea about the proposed analytical method while I was presenting the problem to my co-workers, and I managed to develop the method the same day before going to sleep, as I was really excited about the idea of the method and about the impact that this method would generate for the performance of the solver I'm developing.

According to the bibliographic research carried out by the authors of the mentioned paper, the problem has not yet been presented in the scientific literature.

However, the mathematical model and, in particular, the analytical method developed for the MPBPTM problem are also very important scientific contributions.

The language used in the paper is simple, so that many researchers can easily understand the work.

I am then waiting for your final decision with great expectation of approval of the work for publication in the Applied Mathematical Modelling journal.	
    \closing{Sincerely,}
  \end{letter}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2023-07-05 (2023) Fraga et al.tex
updating files

@@
 
-\section{Multiproduct batch processing time maximization problem}
+\section{Multi-product batch processing time maximization problem}
 \label{sec:MBPTMP}
 
-The multiproduct batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (prodction rate) for each product.
+The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
+In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
 In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
@@
 
-In this paper we presented the Multi-product Batch Processing Time Maximization Problem, as well as a mathematical model and an analytical solution method for this problem.
+In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an analytical solution method for this problem.
 The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.

### 2023-07-14 (2023) Fraga et al.tex
updating files

@@
 
-%\affiliation{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
-%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
-%             city={Caruaru},
-%             postcode={55014-900},
-%             state={PE},
-%             country={Brasil}}
+\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
+\ead{tatiana.balbi@ufpe.br}
+\cortext[cor1]{corresponding author}
+
+\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
+\ead{italo_ruan_@hotmail.com}
+
+\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
+\ead{regilda.smenezes@ufpe.br}
+
+\affiliation[label1]{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
+             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
+             city={Caruaru},
+             postcode={55014-900},
+             state={PE},
+             country={Brasil}}
 
@@
 
-As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution method for solving this problem.
+As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.
 
@@
 
-\section{Analytical solution}
+\section{Fraga's analytical solution}
 \label{sec:analyticalSol}
@@
 \end{tabular}
-\caption{Benchmark MBPTMP 001}
+\caption{Benchmark MPBPTMP 001}
 \label{tab:MBPTMP001}
@@
 \end{tabular}
-\caption{Benchmark MBPTMP 002}
+\caption{Benchmark MPBPTMP 002}
 \label{tab:MBPTMP002}
@@
 \end{tabular}
-\caption{Benchmark MBPTMP 003}
+\caption{Benchmark MPBPTMP 003}
 \label{tab:MBPTMP003}
@@
 \cline {1-5} \\
-MBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
-MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
-MBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
-RMBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
-RMBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
-RMBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
-RMBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
-RMBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
+MPBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
+MPBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
+MPBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
+RMPBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
+RMPBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
+RMPBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
+RMPBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
+RMPBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
 \cline {1-5} \\

### 2023-07-27 cover.tex
updating files

@@
 
-\begin{letter}{To Applied Mathematical Modelling journal}
+\begin{letter}{To Simulation Modelling Practice and Theory}
     \setkomavar{subject}{Cover letter}
@@
 
+MPBPTM is a combinatorial optimization problem.
+The complexity of MPBPTM is mainly attributed to the fact that there is a production limit for the set of products and not just for each product.
+This restriction causes the problem to be defined as a non-polynomial problem.
+
 The problem was identified by me during the development of a solver for production planning in extruders.
-
 As I am applying a local search heuristic, at each iteration I need to generate a new solution, and therefore I need to solve the MPBPTM problem.
 
-I had a vague idea about the proposed analytical method while I was presenting the problem to my co-workers, and I managed to develop the method the same day before going to sleep, as I was really excited about the idea of the method and about the impact that this method would generate for the performance of the solver I'm developing.
+However, MPBPTM is also a practical problem and its solution directly influences the efficiency of inventory control in some industries, as is the case of industries in the plastic bag sector.
 
-According to the bibliographic research carried out by the authors of the mentioned paper, the problem has not yet been presented in the scientific literature.
+As is widely known, there are few combinatorial optimization problems that can be solved using exact methods.
+In this paper we present an exact optimization method for solving the MPBPTM problem, based on the idea of partitioning the problem into two smaller problems.
 
-However, the mathematical model and, in particular, the analytical method developed for the MPBPTM problem are also very important scientific contributions.
+I had a vague idea about the proposed method while I was presenting the problem to my co-workers, and I managed to develop the method the same day before going to sleep, as I was really excited about the idea of the method and about the impact that this method would generate for the performance of the solver I'm developing for production planning in extruders.
 
-The language used in the paper is simple, so that many researchers can easily understand the work.
+According to the bibliographic research carried out by the authors, the problem and exact method proposed in this paper has not yet been presented in the scientific literature.
 
-I am then waiting for your final decision with great expectation of approval of the work for publication in the Applied Mathematical Modelling journal.	
+Also, the language used in the paper is simple, so that many researchers can easily understand the work.
+
+I am then waiting for your final decision with great expectation of approval of the work for publication in this journal.	
     \closing{Sincerely,}

### 2023-07-27 manuscript.tex
updating files

--- 2023-07-14 (2023) Fraga et al.tex
@@
 \begin{frontmatter}
-
 %% Title, authors and addresses
@@
 
-\affiliation[label1]{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
-             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
+%\affiliation[label1]{
+%			 organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
+%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
+%             city={Caruaru},
+%             postcode={55014-900},
+%             state={PE},
+%             country={Brasil} }
+
+\affiliation[label1]{
+		   organization={Agreste Academic Center - Federal University of Pernambuco},%Department and Organization
+           addressline={Avenida Marielle Franco, Nova Caruaru}, 
            city={Caruaru},
@@
            state={PE},
-             country={Brasil}}
-
-%\affiliation{organization={},%Department and Organization
-%            addressline={}, 
- %           city={},
- %           postcode={}, 
- %           state={},
- %          country={}}
+           country={Brazil}}
 
@@
 \end{abstract}
-
 %%Graphical abstract
 \begin{graphicalabstract}
-\includegraphics[width=13cm]{graphical.png}
+\includegraphics[width=0.8\textwidth]{graphical.png}
 \end{graphicalabstract}
@@
 \item linear integer programming model for the MPBPTM problem;
-\item polynomial time complexity analytical method for solving the MPBPTM problem.
+\item exact optimization method for solving the MPBPTM problem.
 \end{highlights}
@@
 multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
 \end{keyword}
-
 \end{frontmatter}
@@
 Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence.
+In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time.
+\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints.
+In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine.
+However, there are no production limitations for the production of each product group.
+The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems.
 Other important works deal with the problem of a multi-product batch plant design (MPBPD).
-In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.
+In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
 
-In this work, we are concerned with determining the ideal processing time for a batch consisting of a set of products, each product being or not different from the other products of the same batch.
+In this work, we are concerned with determining the ideal processing time for a single batch consisting of a set of products, each product being or not different from the other products of the same batch.
 That is, we consider a specific case where different products are processed simultaneously on the same processor.
@@
 
-\section{Fraga's analytical solution}
+\section{Analytical solution}
 \label{sec:analyticalSol}
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ (https://github.com/blinded) and a solver in LINGO (https://github.com/blinded).
+To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (https://github.com/tbfraga/COPSolver).
 The tests were performed on a notebook with an Intel i7 processor.
@@
 
-\section{Contributions to this work}
-\label{sec:contributions}
-
-The work for the elaboration of this paper was carried out by tree contributors, as described below.
-Blinded, developed the detailed study on the plastic bag production process, which made it possible to identify the problem addressed in this paper.
-Blinded was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for applying the analytical solution and a solver in LINGO for validating the mathematical model and the results found by the first solver, developing benchmarks, and testing the model and analytical method proposed, as well as surveying bibliography and elaboration of the paper.
-Blinded contributed to the bibliographic survey.
-The authorship of this work is distributed according to contributions described.
-
 \section{Conclusions and suggestions for future works}
@@
 
+\section{CRediT authorship contribution statement} 
+\label{sec:contributions}
+
+T.B.
+Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
+Í.R.B.
+Aquino: Data curation.
+R.C.S.
+Menêzes: Data curation.
+
 \section{Acknowledgments}
@@
 
-Blinded.
-%We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
+We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
 We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
@@
 
+\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
+Li, C., Wang, F., Gupta, J.N.D., Chung, T.
+(2022).
+Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints.
+{\it Computers \& Industrial Engineering}, Vol.
+169, pp.
+108115.
+
 \bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}

### 2023-07-31 multi-period/manuscript.tex
updating paper
constructing math model

--- 2023-07-27 manuscript.tex
@@
 
-\title{Multi-product Batch Processing Time Maximization Problem}
+\title{Multi-period and Multi-product Batch Processing Time Maximization Problem}
 
@@
 
-%\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}
+%\author{Tatiana Balbi Fraga}
 
@@
 \cortext[cor1]{corresponding author}
-
-\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
-\ead{italo_ruan_@hotmail.com}
-
-\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
-\ead{regilda.smenezes@ufpe.br}
-
-%\affiliation[label1]{
-%			 organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
-%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
-%             city={Caruaru},
-%             postcode={55014-900},
-%             state={PE},
-%             country={Brasil} }
 
@@
 \begin{abstract}
-In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates.
-The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch.
-In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem.
-We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
+...
 \end{abstract}
@@
 \begin{graphicalabstract}
-\includegraphics[width=0.8\textwidth]{graphical.png}
+%\includegraphics[width=0.8\textwidth]{graphical.png}
 \end{graphicalabstract}
@@
 \begin{highlights}
-\item brief bibliographic review on multi-product batch problems;
-\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
-\item linear integer programming model for the MPBPTM problem;
-\item exact optimization method for solving the MPBPTM problem.
+\item ...;
+\item ...;
+\item ...;
+\item ....
 \end{highlights}
@@
 \begin{keyword}
-multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
+multiproduct batch \sep processing time maximization \sep C++ \sep LINGO
 \end{keyword}
@@
 
-The scientific literature presents several papers that address multi-product batch problems.
-Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
-In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed.
-The solution must be determined in such a way that both setup and storage costs are minimized.
-Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
-\cite{MendezEtAll2000} and \cite{ShiEtAll2017} present two parallel multi-product batch scheduling (PMPBS) problems, in which production units of the same type are arranged in parallel, forming each production stage.
-In this case, it is also necessary to define in which units each product will be processed.
-The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance).
-In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages.
-\cite{KimEtAl1996} consider the multi-product batch problem in networked processes.
-As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist.
-Therefore, the production paths in the flowshop network can be different for each product.
-Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence.
-In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time.
-\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints.
-In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine.
-However, there are no production limitations for the production of each product group.
-The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems.
-Other important works deal with the problem of a multi-product batch plant design (MPBPD).
-In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
+T....
 
-In this work, we are concerned with determining the ideal processing time for a single batch consisting of a set of products, each product being or not different from the other products of the same batch.
-That is, we consider a specific case where different products are processed simultaneously on the same processor.
-This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.
-
-As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.
+As scientific contributions,....
 
@@
 
-\section{Multi-product batch processing time maximization problem}
+\section{Multi-period and multi-product batch processing time maximization problem}
 \label{sec:MBPTMP}
 
-The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
-In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
-The maximum production quantity of each product is mainly defined according to the demand for the product.
-However, it is still possible to stock the products and/or send them to the outlets.
-In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
-Also, there is a time limit available for processing the batch.
-The problem consists of defining the maximum processing time for the batch, respecting the limitations related to the quantities produced.
-For a better understanding of the problem, an example is presented below.
+In MPMPBPTM problem consideramos um horizonte de planejamento com $\textrm{ND}$ dias ($\textrm{ND} \geq 1$) e uma demanda diária ($\textrm{UD}_{id} \geq 0$) durante este período para cada produto do lote considerado.
+Adicionalmente, já existe um plano de produção prévio, de forma que é possível que já exista uma programação anterior de produção para cada produto do lote.
+Assim a disponibilidade para estocagem e para envios para as lojas de fábrica ficará sujeita a alteração de acordo com o planejamento prévio de produção.
 
-\emph{Example:} A certain machine must process a batch containing 2 different products: A and B.
-The production rate of A is 60 g/min while the production rate of B is 40 g/min.
-The factory has free stock for a maximum of 3000 g of any product, and, according to the company's inventory policy, a maximum of 3000 g of product A and 2000 g of product B can be stocked at the factory.
-There is a demand for 1000 g of product A and 500 g of product B.
-The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.
-A maximum time of 100 minutes of this machine can be allocated for processing this batch.
-What is the maximum possible time for processing this batch ?
+O problema consiste em determinar a tempo máximo de processamento para o lote considerado, levando em conta as restrições de limite consideradas.
+
+A seção a seguir apresenta um modelo matemático para este problema.
 
@@
 
-$\textrm{UD}_i$ is the demand for the product $i$;
+$\textrm{UD}_{id}$ is the demand for the product $i$ on day $d$;
 
-$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;
+$\textrm{PO}_{id}$ is the planned production of the product $i$ on day $d$;
 
-$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;
+$\textrm{I}_{0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;
+
+$\textrm{UI}_{i0}$ is the maximum quantity allowed for stocking in the factory the product $i$ on the (\emph{first}) planning day; \\
+
+$\textrm{I}_{id}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;
+
+$\textrm{UI}_{id}$ is the maximum quantity allowed for stocking in the factory the product $i$ on day $d$;
 
@@
 
-$\textrm{Z}$ is the timeout for batch processing;
+$\textrm{Z}$ is the timeout for batch processing; \\
 
-$P_i$ is the amount of product $i$ produced;
+$P_i$ is the amount of product $i$ to be produced on batch;
 
-$D_i$ is the amount of product $i$ delivered for the demand;
+$D_{id}$ is the amount of product $i$ delivered for the demand on day $d$;
 
-$O_i$ amount of product $i$ shipped to factory outlets;
+$O_{id}$ amount of product $i$ shipped to factory outlets;
 
-$I_i$ is the amount of product $i$ that will be stored at the factory;
+$I_{id}$ is the amount of product $i$ that will be stored at the factory on day $d$;
 
@@
 \begin{equation}
-P_i - D_i - O_i - I_i = 0 \quad \forall i
+P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{I}_{0} - \textrm{PO}_{i1}
 \end{equation}
@@
 \begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
+UI_{id} - UI_{i(d-1)} - D_{id} - O_{id} = - \textrm{PO}_{id} \quad \forall i, \forall (d>1)
 \end{equation}
@@
 \begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
 \end{equation}
@@
 \begin{equation}
-\sum_i{O_i} \leq \textrm{O}
+\sum_{d}{O_{id}} \leq \textrm{UO}_i \quad \forall i
 \end{equation}
@@
 \begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
+\sum_{i}{\sum_{d}{O_{id}}} \leq \textrm{O}
 \end{equation}
@@
 \begin{equation}
-\sum_i{I_i} \leq \textrm{I}
+D_{i1} \leq \textrm{UD}_{i1} \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_{id} \leq \sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}  \quad \forall i, \forall d>1
 \end{equation}
@@
 \begin{equation}
-T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
+UI_{id}, O_{id}, D_{id} \in  \mathbb{Z}^+ \quad \forall i,d
 \end{equation}

### 2023-07-31 multi-period/manuscript.tex
updating paper
math model

@@
 
-$\textrm{I}_{0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;
+$\textrm{UI}_{i0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;
 
@@
 
-$\textrm{I}_{id}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;
+$\textrm{I}_{d}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;
 
@@
 \begin{equation}
-P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{I}_{0} - \textrm{PO}_{i1}
+P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i0} - \textrm{PO}_{i1}
 \end{equation}
@@
 \begin{equation}
+I_{1} + \sum_{i}\{P_i -  D_{i1} - O_{i1}\} = \textrm{I}_{0} 
+\end{equation}
+
+\begin{equation}
+I_{d} - I_{d-1} + \sum_{i}\{P_i -  D_{id} - O_{id}\} = 0 \quad \forall (d>1)
 \end{equation}
@@
 \begin{equation}
-UI_{id}, O_{id}, D_{id} \in  \mathbb{Z}^+ \quad \forall i,d
+UI_{id}, I_{d}, O_{id}, D_{id} \in  \mathbb{Z}^+ \quad \forall i,d
+\end{equation}
+
+\begin{equation}
+I_{d} \in  \mathbb{Z}^+ \quad \forall d
 \end{equation}
@@
 Aquino: Data curation.
-R.C.S.
-Menêzes: Data curation.
 

### 2023-07-31 multi-period/manuscript.tex
updating paper
math model

@@
 
-$\textrm{UI}_{i0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;
-
-$\textrm{UI}_{i0}$ is the maximum quantity allowed for stocking in the factory the product $i$ on the (\emph{first}) planning day; \\
-
-$\textrm{I}_{d}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;
-
-$\textrm{UI}_{id}$ is the maximum quantity allowed for stocking in the factory the product $i$ on day $d$;
-
 $\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;
@@
 
+$UI_{id}$ is the maximum quantity allowed for stocking in the factory the product $i$ on day $d$;
+
+being $\textrm{UI}_{i0}$ the maximum quantity allowed for stocking in the factory the product $i$ on the (\emph{first}) planning day ($d=1$);
+
+$I_{d}$ is the free factory storage of all products on the end of the day $d$;
+
+being $\textrm{I}_{0}$ the initial free inventory for all products on factory on the start of the (\emph{first}) planning day ($d=1$); \\
+
 $P_i$ is the amount of product $i$ to be produced on batch;
@@
 $O_{id}$ amount of product $i$ shipped to factory outlets;
-
-$I_{id}$ is the amount of product $i$ that will be stored at the factory on day $d$;
 

### 2023-08-02 multi-period/manuscript.tex
including an example for the MPMPBPTM problem

@@
 Assim a disponibilidade para estocagem e para envios para as lojas de fábrica ficará sujeita a alteração de acordo com o planejamento prévio de produção.
+O problema consiste em determinar a tempo máximo de processamento para o lote considerado, levando em conta as restrições de limite consideradas.
+For a better understanding of the problem, an example is presented below.
+\\
 
-O problema consiste em determinar a tempo máximo de processamento para o lote considerado, levando em conta as restrições de limite consideradas.
+\emph{Example:} A certain machine must process a batch containing 2 different products: A and B.
+The production rate of A is 60 g/min while the production rate of B is 40 g/min.
+The factory has free stock for a maximum of 3000 g of any product, and, according to the company's inventory policy, a maximum of 3000 g of product A and 2000 g of product B can be stocked at the factory.
+For the first day, there is a demand for 1000 g of product A and 500 g of product B, and for the second day, there is a demand for 500 g of product A and 300 g of product B.
+The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.There is a previous production planning for 1000 units of product A for the first day and 800 units of product B for the second day.
+A maximum time of 100 minutes of this machine can be allocated for processing this batch.
+What is the maximum possible time for processing this batch ?
+\\
 
@@
 \label{sec:analyticalSol}
-
-It is possible to consider the factory stock and the outlets stock as single stock, so we have:
-
-\begin{equation}
-E_i = O_i + I_i
-\end{equation}
-
-where $E_i$ is the sum of the quantity stored at the factory and the quantity sent to the outlets of the product $i$. \\
-
-So that:
-
-\begin{equation}
-E_i \leq \textrm{UO}_i + \textrm{UI}_i
-\end{equation}
-
-and
-
-\begin{equation}
-\sum_i {E_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-It is also possible to split the batch processing time into two time slots:
-
-\begin{equation}
-T = T' + T''
-\end{equation}
-
-and consider that $T'$ is the maximum processing time used only for production that will meet the demand. Thus, we can find $T'$, solving the reduced problem:
-
-\begin{equation}
-max \quad T'
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-D_i - \textrm{p}_i * T'  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i, T' \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-This reduced problem can be rewritten in the form:
-
-\begin{equation}
-max \quad T'
-\end{equation}
-
-$s.t.$ \\
-
-\begin{equation}
-T'  \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
-\end{equation}
-
-So we have that $T'$ will be the smallest of the ratios $\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor$ of all products. \\
-
-Once we find the value of $T'$, we can calculate the value of unmet demand for each product after $T'$, $S_i$, through the equations in (\ref{eq:unmet1}).
-
-\begin{equation}
-\label{eq:unmet1}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-Now we consider that the time interval $T''$ will be used for the production of the quantities that will be stored (in the factory and in the outlets), as well as of the demand not met by the production in the first time interval, $S_i$.
-
-In this case, we can find $T'''$ by solving the second reduced problem:
-
-\begin{equation}
-max \quad T''
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-E_i - \textrm{p}_i * T''  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-E_i - S_i \leq \textrm{UO}_i + \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i {E_i - S_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-\begin{equation}
-E_i, T'' \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-Again, using a little algebra, we can rewrite this reduced problem in the form:
-
-\begin{equation}
-max \quad T''
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-T'' \leq \lfloor{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i}\rfloor  \quad \forall i
-\end{equation}
-
-\begin{equation}
-T'' \leq \lfloor{(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}}\rfloor
-\end{equation}
-
-So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.
-\\
-
-So, the analytical method can be decomposed into 4 steps: \\
-
-step 1: find $T'$, where:
-\begin{equation}
-T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
-\end{equation}
-
-step 2: calculate $S_i$ for all products.
-\begin{equation}
-\label{eq:unmet}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-step 3: find $T''$, where:
-\begin{equation}
-T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 4: calculate $T$, where: 
-\begin{equation}
-T = T' + T''
-\end{equation}
-\begin{equation}
-T = \min \{T , \textrm{Z}\}
-\end{equation}
 

### 2023-08-02 multi-period/manuscript.tex
elaborating solution method for a multi-period problem

@@
 For the first day, there is a demand for 1000 g of product A and 500 g of product B, and for the second day, there is a demand for 500 g of product A and 300 g of product B.
-The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.There is a previous production planning for 1000 units of product A for the first day and 800 units of product B for the second day.
+The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.
+There is a previous production planning for 1000 units of product A for the first day and 1500 units of product B for the second day.
 A maximum time of 100 minutes of this machine can be allocated for processing this batch.
@@
 \begin{equation}
+\label{eq:mmeq02}
 P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i0} - \textrm{PO}_{i1}
@@
 \begin{equation}
+\label{eq:mmeq03}
 UI_{id} - UI_{i(d-1)} - D_{id} - O_{id} = - \textrm{PO}_{id} \quad \forall i, \forall (d>1)
@@
 \begin{equation}
-I_{1} + \sum_{i}\{P_i -  D_{i1} - O_{i1}\} = \textrm{I}_{0} 
+I_{1} + \sum_{i}\{P_i -  D_{i1} - O_{i1}\} = \textrm{I}_{0} - \sum_{i}{\textrm{PO}_{i1}}
 \end{equation}
@@
 \begin{equation}
-I_{d} - I_{d-1} + \sum_{i}\{P_i -  D_{id} - O_{id}\} = 0 \quad \forall (d>1)
+I_{d} - I_{d-1} + \sum_{i}\{P_i -  D_{id} - O_{id}\} = - \sum_{i}{\textrm{PO}_{id}} \quad \forall (d>1)
 \end{equation}
@@
 \begin{equation}
+\label{eq:mmeq09}
 D_{i1} \leq \textrm{UD}_{i1} \quad \forall i
@@
 
-\section{Analytical solution}
-\label{sec:analyticalSol}
+\section{Exact optimizatin method}
+\label{sec:method}
 
-It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper. \\
+Uma solução ótima para este problema pode ser construída através de duas etapas, conforme explicado a seguir: \\
+
+\emph{etapa 1: construção do MPBPTMP} \\
+
+passo 1: Desconsidere a produção a ser planejada:
+
+\begin{equation}
+\label{eq:sm01}
+P_i = 0, \forall i
+\end{equation}
+
+passo 2: Calcule os valores $D_{id}^+$, $D_{id}^-, \forall i, d$, usando as equações em (\ref{eq:sm02}) e (\ref{eq:sm03}):
+
+\begin{equation}
+\label{eq:sm02}
+D_{id}^+ = \sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}  \quad \forall i, \forall d>1
+\end{equation}
+
+\begin{equation}
+\label{eq:sm03}
+D_{id}^- = \sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}  \quad \forall i, \forall d>1
+\end{equation}
+
+Calcule $D_{i1}$ usando as equações em (\ref{eq:sm04}):
+
+\begin{equation}
+\label{eq:sm04}
+D_{i1} = \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\} \quad \forall i
+\end{equation}
+
+queremos encontrar $D_{id}$, tal que a equação em (\ref{eq:sm04}) seja respeitada:
+
+\begin{equation}
+\label{eq:sm04}
+D_{id} = \min {x \in \{D_{id}^-, D_{id}^+\}} \textrm{ tal que } UI_{id} \geq 0
+\end{equation}
+
+Contudo, inicialmente iremos adotar:
+
+\begin{equation}
+\label{eq:sm04}
+D_{id} = D_{id}^- \quad \forall i, \forall d>1
+\end{equation}
+
+e calcule os valores de $D_{id}$ e $O_{id}, \forall i, d$.
+
+Inicialmente desconsidere a produção a ser planejada fazendo $P_i = 0, \forall i$, e
+
+Tais valores podem ser calculados da seguinte forma:
+
+- distribua a produção previamente planejada para atender à demanda seguindo as restrições em (9) e para as duas equações derivadas de (10):
+
+as restrições em (14), (15) e (16) foram criadas porque queremos permitir que a demanda referênte ao dia atual seja atendida pela produção planejada para o dia atual e não por produções futuras.
+
+- distribua o restante da produção previamente planejada, se houver, para os outlests respeitando as restrições em (7) e (8).
+
+- faça $D_{id} = D_{id}^- \quad \forall i$;
+
+- calcule os valores para $UI_{id}, \forall i, d$, usando as equações em (3) e (4).
+
+- calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6).
+
+- recalcule o valor de $D_{id}$, usando:
+
+\begin{equation}
+D_{id} = D_{id}^- - \max\{0, UI_{id}\} \quad \forall i, d>0
+\end{equation}
+
+E então recalcule $UI_{id}, \forall i, (d>1)$, usando as equações em (4).
+
+Então, com base nos valores claculado, construímo o problema MPBPTM, usando as equações:
+
+\begin{equation}
+\textrm{UD}_{i} = \textrm{UD}_{i1} - D_{i1}, \quad \forall i
+\end{equation}
+
+\begin{equation}
+\textrm{I} = \min_{d} \{I_{d}\}
+\end{equation}
+
+\begin{equation}
+\textrm{UI}_{i} = \min_{d} \{UI_{id}\}, \quad \forall{i}
+\end{equation}
+
+\begin{equation}
+\textrm{O} = \textrm{O} - \sum_{i}{\sum_{d}{O_{id}}}
+\end{equation}
+
+\begin{equation}
+\textrm{UO}_{i} = \textrm{UO}_{i} - \sum_{d}{O_{id}}, \quad \forall i
+\end{equation} \\
+
+Sendo $\textrm{p}_{i}$ e $\textrm{Z}$ definidos de acordo com o problema apresentado.
+
+E resolvemos esse novo problema usando o método de partição do tempo proposto por Fraga (Fraga et al., 2023).\\
 
@@
 
-$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
+Como planejamento prévio de produção, temos:
 
-$T' \leq 16 \textrm{ min}$ \quad for A \\
+$\textrm{P}_{11} = 1000$,
+$\textrm{P}_{12} = 0$,
+$\textrm{P}_{21} = 0$,
+$\textrm{P}_{22} = 1500$. \\
 
-$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
+Como demanda, temos:
 
-$T' \leq 12 \textrm{ min}$ \quad for B \\
+$\textrm{UD}_{11} = 1000$,
+$\textrm{UD}_{12} = 500$,
+$\textrm{UD}_{21} = 500$,
+$\textrm{UD}_{22} = 300$. \\
 
-so: \\
+Distribuindo a produção para atender à demanda de acordo com as restrições em (9) e (10), temos: \\
 
-$T' = 12 \textrm{ min}$ \\
+$D_{11} = 1000$,
+$D_{12} = 0$,
+$D_{21} = 0$,
+$D_{22} = 300$. \\
+
+Não há nenhuma sobra relativa a produção de A. E há uma sobra de produção de 1200 unidades de B no segundo dia. \\
+
+Como estoque livre nos outlets, temos:
+
+$\textrm{UO}_{1} = 600$;
+$\textrm{UO}_{2} = 600$;
+$\textrm{O} = 1000$; \\
+
+Assim, distribuindo a sobra da produção para os outlets de acordo com as restrições em (7) e (8), temos:
+
+$O_{11} = 0$,
+$O_{12} = 0$,
+$O_{21} = 0$,
+$O_{22} = 600$. \\
+
+Com relação ao estoque livre em fábrica, temos:
+
+$\textrm{UI}_{10} = 3000$,
+$\textrm{UI}_{20} = 2000$,
+$\textrm{I}_{0} = 3000$. \\
+
+Portanto, calculando os valores disponíveis para produção de acordo com as equações em (3), (4) e (5), temos:
+
+$UI_{11} = 3000 - 1000 + 1000 + 0 =  3000$,
+$UI_{12} = 3000 - 0 + 0 + 0 =  3000$,
+$UI_{21} = 2000 - 0 + 0 + 0 =  2000$,
+$UI_{22} = 2000 - 1500 + 300 + 600 =  1400$. \\
+
+$I_{1} = 3000 - 1000 + 1000 + 0 = 3000$,
+$I_{2} = 3000 - 1500 + 300 + 600 = 2400$. \\
+
+Portanto temos agora as informações referentes aos limites estocagem em fábrica diário para cada produto assim como o limite de estocagem em fábrica diário para todos os produtos. \\
+
+Definindo o problema MPBPTM, temos: \\
+
+$\textrm{UD}_{1} = 1000 - 1000 = 0$,
+$\textrm{UD}_{2} = 0$ . \\
+
+$\textrm{I} = \min_{d} \{3000, 2400\} = 2400$. \\
+
+$ \textrm{UI}_{1} = \min_{d} \{3000, 3000\} = 3000 $,
+$ \textrm{UI}_{2} = \min_{d} \{2000, 1400\} = 1400 $. \\
+
+$\textrm{O} = 1000 - 600 = 400.$ \\
+
+$\textrm{UO}_{1} = 600 - 0 = 600$, 
+$\textrm{UO}_{2} = 600 - 600 = 0$. \\
+
+$\textrm{p}_{1} = 60$,
+$\textrm{p}_{2} = 40$.  \\
+
+$\textrm{Z} = 100$.  \\
+
+Então, aplicando o método de partição do tempo proposto pro Fraga, temos: \\
+
+$T' = 0 \textrm{ min}$ \\
 
@@
 
-$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$ \\
+$S_A = 0 \textrm{ g}$ \\
 
-$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$ \\
+$S_B = 0 \textrm{ g}$ \\
 
@@
 
-$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
+$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 0 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T'' \leq 64 \textrm{ min}$ \quad for A \\
+$T'' \leq 60 \textrm{ min}$ \quad for A \\
 
-$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
+$T'' \leq \lfloor{(1400 \textrm{ g} + 0 \textrm{ g} + 0 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T'' \leq 65 \textrm{ min}$ \quad for B \\
+$T'' \leq 35 \textrm{ min}$ \quad for B \\
 
-$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\
+$T'' \leq \lfloor{(400 \textrm{ g} + 2400 \textrm{ g} + 0 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\
 
-$T'' \leq 43 \textrm{ min}$ \quad for A and B \\
+$T'' \leq 28 \textrm{ min}$ \quad for A and B \\
 
@@
 
-$T'' = 43 \textrm{ min}$ \\
+$T'' = 28 \textrm{ min}$ \\
 
@@
 
-$T = 55 \textrm{ min}$ \\
+$T = 28 \textrm{ min}$ \\
 
-As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution. \\
+As $T<\textrm{Z}$, then $T = 28 \textrm{ min}$ will certainly be the optimal solution. \\
 
@@
 
-$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$ \\
+$P_A = 1,680  \textrm{ g}$ e $P_B=1,120 \textrm{ g}$ \\
 
-$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$ \\
+$D_A = 0 \textrm{ g}$ e $D_B = 0 \textrm{ g}$ \\
 
-$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$ \\
-
-Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the undetermined system of inequalities:
-
-\begin{equation}
-O_i + I_i = E_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{O_i} \leq \textrm{O}
-\end{equation}
-
-\begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{I_i} \leq \textrm{I}
-\end{equation}
-
-\begin{equation}
-O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
+$E_A = 1,680 \textrm{ g}$ e $E_B = 1,120 \textrm{ g}$ \\
 
@@
 Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
-We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.
 

### 2023-08-02 multi-period/manuscript.tex
exact method
developing

@@
 \begin{equation}
-\label{eq:mmeq02}
+\label{eq:mmeq03}
 P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i0} - \textrm{PO}_{i1}
@@
 \begin{equation}
-\label{eq:mmeq03}
+\label{eq:mmeq04}
 UI_{id} - UI_{i(d-1)} - D_{id} - O_{id} = - \textrm{PO}_{id} \quad \forall i, \forall (d>1)
@@
 \begin{equation}
+\label{eq:mmeq05}
 I_{1} + \sum_{i}\{P_i -  D_{i1} - O_{i1}\} = \textrm{I}_{0} - \sum_{i}{\textrm{PO}_{i1}}
@@
 
-passo 2: Calcule os valores $D_{id}^+$, $D_{id}^-, \forall i, d$, usando as equações em (\ref{eq:sm02}) e (\ref{eq:sm03}):
+passo 2:
+
+Calcule $D_{i1}$ usando as equações em (\ref{eq:sm02}):
 
@@
 \label{eq:sm02}
-D_{id}^+ = \sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}  \quad \forall i, \forall d>1
+D_{i1} = \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\} \quad \forall i
+\end{equation}
+
+Calcule o valor da sobra da produção não distribuída, $\textrm{S}_{id}, \forall i$, pelas equações em (\ref{eq:sm03}) e (\ref{eq:sm04}):
+
+\begin{equation}
+\label{eq:sm03}
+\textrm{S}_{i1} = \textrm{PO}_{i1} - D_{i1}, \quad \forall i
 \end{equation}
@@
 \begin{equation}
-\label{eq:sm03}
-D_{id}^- = \sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}  \quad \forall i, \forall d>1
+\label{eq:sm04}
+\textrm{S}_{id} = \textrm{PO}_{id}, \quad \forall i, (d>1)
 \end{equation}
 
-Calcule $D_{i1}$ usando as equações em (\ref{eq:sm04}):
+Calcule os valores $D_{id}^+$ e $D_{id}^-, \forall i, d$, usando ambas as equações entre (\ref{eq:sm05}) e (\ref{eq:sm08}) aplicando essas quatro equações de forma ordenada e progressiva em relação à $d$, ou seja, primeiro as equações (\ref{eq:sm05}) e (\ref{eq:sm07})  para $d = 2$, depois as equações (\ref{eq:sm06}) e (\ref{eq:sm08}) para $d = 2$, em seguida as equações (\ref{eq:sm05}) e (\ref{eq:sm07}) para $d=3$, depois depois as equações (\ref{eq:sm06}) e (\ref{eq:sm08}) para $d = 3$, etc.
 
 \begin{equation}
-\label{eq:sm04}
-D_{i1} = \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\} \quad \forall i
+\label{eq:sm05}
+D_{id}^+ =  \min\{(\sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}), \sum_{k=1}^{d}{\textrm{S}_{ik}^+}\}  \quad \forall i, \forall (d>1)
 \end{equation}
 
-queremos encontrar $D_{id}$, tal que a equação em (\ref{eq:sm04}) seja respeitada:
+\begin{equation}
+\label{eq:sm06}
+\textrm{S}_{id}^+ = \textrm{PO}_{id} - D_{id}^+, \quad \forall i, \forall (d>1)
+\end{equation}
 
 \begin{equation}
-\label{eq:sm04}
-D_{id} = \min {x \in \{D_{id}^-, D_{id}^+\}} \textrm{ tal que } UI_{id} \geq 0
+\label{eq:sm07}
+D_{id}^- =  \min\{(\sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=2}^{d-1}{D_{ik}}), \sum_{k=1}^{d}{\textrm{S}_{ik}^-}\}  \quad \forall i, \forall (d>1)
+\end{equation}
+
+\begin{equation}
+\label{eq:sm08}
+\textrm{S}_{id}^- = \textrm{PO}_{id} - D_{id}^-, \quad \forall i, \forall (d>1)
+\end{equation}
+
+Queremos encontrar $D_{id}, \forall i,(d>1)$, tal que as restrições em (\ref{eq:sm09}) sejam respeitadas:
+
+\begin{equation}
+\label{eq:sm09}
+D_{id} = \min {x \in \{D_{id}^-, D_{id}^+ \quad | \quad UI_{id} \geq 0\}} \quad \forall i, \forall (d>1)
 \end{equation}
@@
 \begin{equation}
-\label{eq:sm04}
-D_{id} = D_{id}^- \quad \forall i, \forall d>1
+\label{eq:sm10}
+D_{id} = D_{id}^- \quad \forall i, \forall (d>1)
 \end{equation}
 
-e calcule os valores de $D_{id}$ e $O_{id}, \forall i, d$.
+\begin{equation}
+\label{eq:sm10}
+\textrm{S}_{id} = \textrm{S}_{id}^- \quad \forall i, \forall (d>1)
+\end{equation}
 
-Inicialmente desconsidere a produção a ser planejada fazendo $P_i = 0, \forall i$, e
+passo 3: Calcule os valores $O_{id}, \forall i, d$, usando as equações em (\ref{eq:sm11}):
 
-Tais valores podem ser calculados da seguinte forma:
+\begin{equation}
+\label{eq:sm11}
+O_{id} = \min \{\textrm{S}_{id}, (\textrm{UO}_i - \sum_{k=1}^{d-1}{O_{ik}}) , (\textrm{O}- \sum_{j=1}^{i-1}\sum_{k=1}^{d-1}{O_{jk}}) \} \quad \forall i, d
+\end{equation}
 
-- distribua a produção previamente planejada para atender à demanda seguindo as restrições em (9) e para as duas equações derivadas de (10):
+passo 4:
 
-as restrições em (14), (15) e (16) foram criadas porque queremos permitir que a demanda referênte ao dia atual seja atendida pela produção planejada para o dia atual e não por produções futuras.
+calcule os valores para $UI_{id}, \forall i, d$, usando as equações em (\ref{eq:mmeq03}) e (\ref{eq:mmeq04})).
 
-- distribua o restante da produção previamente planejada, se houver, para os outlests respeitando as restrições em (7) e (8).
-
-- faça $D_{id} = D_{id}^- \quad \forall i$;
-
-- calcule os valores para $UI_{id}, \forall i, d$, usando as equações em (3) e (4).
-
-- calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6).
+calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6).
 

### 2023-08-04 multi-period/manuscript.tex
improving method
UI_i calculation explanation

@@
 
-In MPMPBPTM problem consideramos um horizonte de planejamento com $\textrm{ND}$ dias ($\textrm{ND} \geq 1$) e uma demanda diária ($\textrm{UD}_{id} \geq 0$) durante este período para cada produto do lote considerado.
-Adicionalmente, já existe um plano de produção prévio, de forma que é possível que já exista uma programação anterior de produção para cada produto do lote.
-Assim a disponibilidade para estocagem e para envios para as lojas de fábrica ficará sujeita a alteração de acordo com o planejamento prévio de produção.
-O problema consiste em determinar a tempo máximo de processamento para o lote considerado, levando em conta as restrições de limite consideradas.
+In MPMPBPTM problem we consider a planning horizon with $\textrm{ND}$ days, ($\textrm{ND} \geq 1$), and a daily demand ($\textrm{UD}_{id} \geq 0$) during this period for each product of the batch.
+Additionally, there is already a prior production plan, so that it is possible that there is already a previous production program for each product of the batch.
+Thus the availability for factory storage and shipping to outlets will be subject to change according to prior production planning.
+The problem is to determine a maximum processing time for the batch, taking into account the restrictions considered.
 For a better understanding of the problem, an example is presented below.
@@
 
-A seção a seguir apresenta um modelo matemático para este problema.
+The following section presents a mathematical model for this problem.
 
@@
 
-being $\textrm{UI}_{i0}$ the maximum quantity allowed for stocking in the factory the product $i$ on the (\emph{first}) planning day ($d=1$);
+being $\textrm{UI}_{i0}$ the maximum quantity allowed for $P_i$;
 
@@
 
-$P_i$ is the amount of product $i$ to be produced on batch;
+$P_i$ is the amount of product $i$ to be produced on batch on the current date (first planning day);
 
@@
 
-\emph{etapa 1: construção do MPBPTMP} \\
+\emph{etapa 1: distribuição da produção previamente planejada} \\
 
@@
 
-Calcule o valor da sobra da produção não distribuída, $\textrm{S}_{id}, \forall i$, pelas equações em (\ref{eq:sm03}) e (\ref{eq:sm04}):
+Calcule o valor da produção não ainda não alocada, $\textrm{S}_{id}, \forall i$, pelas equações em (\ref{eq:sm03}):
 
@@
 
+Calcule os valores $D_{id}^+$, $\textrm{S}_{id}^+$, $D_{id}^-$ e $\textrm{S}_{id}^-, \forall i$, usando as equações de (\ref{eq:sm04}) à (\ref{eq:sm08}).
+
 \begin{equation}
 \label{eq:sm04}
-\textrm{S}_{id} = \textrm{PO}_{id}, \quad \forall i, (d>1)
+D_{i1}^+ = D_{i1}^- = D_{i1}
 \end{equation}
-
-Calcule os valores $D_{id}^+$ e $D_{id}^-, \forall i, d$, usando ambas as equações entre (\ref{eq:sm05}) e (\ref{eq:sm08}) aplicando essas quatro equações de forma ordenada e progressiva em relação à $d$, ou seja, primeiro as equações (\ref{eq:sm05}) e (\ref{eq:sm07})  para $d = 2$, depois as equações (\ref{eq:sm06}) e (\ref{eq:sm08}) para $d = 2$, em seguida as equações (\ref{eq:sm05}) e (\ref{eq:sm07}) para $d=3$, depois depois as equações (\ref{eq:sm06}) e (\ref{eq:sm08}) para $d = 3$, etc.
 
@@
 \label{eq:sm05}
-D_{id}^+ =  \min\{(\sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}), \sum_{k=1}^{d}{\textrm{S}_{ik}^+}\}  \quad \forall i, \forall (d>1)
+D_{id}^+ =  \min\{(\sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}), (\sum_{k=1}^{d-1}{(\textrm{PO}_{ik} - D_{ik}^+) + \textrm{PO}_{id}})\}  \quad \forall i, \forall (d>1)
 \end{equation}
@@
 \label{eq:sm07}
-D_{id}^- =  \min\{(\sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=2}^{d-1}{D_{ik}}), \sum_{k=1}^{d}{\textrm{S}_{ik}^-}\}  \quad \forall i, \forall (d>1)
+D_{id}^- =  \min\{(\sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=2}^{d-1}{D_{ik}}), (\sum_{k=1}^{d-1}{(\textrm{PO}_{ik} - D_{ik}^-) + \textrm{PO}_{id}})\}  \quad \forall i, \forall (d>1)
 \end{equation}
@@
 
-Queremos encontrar $D_{id}, \forall i,(d>1)$, tal que as restrições em (\ref{eq:sm09}) sejam respeitadas:
+Queremos encontrar $D_{id}$, $ D_{id}^- \leq D_{id} \leq D_{id}^+, \forall i,(d>1) $, tal que as restrições em (\ref{eq:sm09}) sejam respeitadas:
 
@@
 
-Contudo, inicialmente iremos adotar:
+Contudo, para solução do problema, iremos adotar:
 
@@
 
-calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6).
+calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6). \\
 
-- recalcule o valor de $D_{id}$, usando:
+\emph{Step 2: MPBPTM problem construction} \\
+
+passo 1: Calcular a quantidade limite para estocagem em fábrica para cada produto, $\textrm{UI}_{i}$.
 
 \begin{equation}
-D_{id} = D_{id}^- - \max\{0, UI_{id}\} \quad \forall i, d>0
+	\max \textrm{UI}_{i}
 \end{equation}
 
-E então recalcule $UI_{id}, \forall i, (d>1)$, usando as equações em (4).
-
-Então, com base nos valores claculado, construímo o problema MPBPTM, usando as equações:
+\emph{sj. to}:
 
 \begin{equation}
-\textrm{UD}_{i} = \textrm{UD}_{i1} - D_{i1}, \quad \forall i
+	\textrm{UI}_{i} \leq UI_{i1}
+\end{equation}
+
+\begin{equation}
+	\textrm{UI}_{i} \leq UI_{id} + \sum_{k=2}^{d}\{\textrm{UD}_{ik} - D_{ik}\}
+\end{equation}
+
+Para compreender a solução proposta, vamos considerar um exemplo:
+
+para 3 dias de planejamento, temos:
+
+dia --> estoque disponível --> demanda não atendida no dia --> soma da demanda não atendida
+
+d1 --> 40
+
+d2 --> 20 --> 10 --> 10
+
+d3 --> 15 --> 5 --> 15
+
+d4 --> 10 --> 0 --> 15
+
+considerando apenas o limite de estoque para o primeiro dia, a parcela da produção que pode ser estocada em fábrica é $40$.
+
+Contudo, esse estoque ficará em fábrica durante todo o período de planejamento considerado, exceto se houver saída para atender à demanda.
+
+Assim, no segundo dia o estoque será igual ao estoque do primeiro dia menos o valor que sairá para atender à demanda acumulada para o dia.
+
+o limite de recebimento de estoque do segundo dia será o limite de estoque mais a demanda não atendida.
+
+Então das 40 unidades estocadas em fábrica no primeiro dia, dez unidades serão entregues à demanda e 30 unidades ficarão estocadas em fábrica.
+
+Como o limite de estoque em fábrica para o segundo dia é de 20 unidades, então isso significa que há 10 unidades excedentes em estoque de fábrica.
+Ou seja, o estoque do primeiro dia, e portanto a produção devem ser diminuídos em 10 unidades.
+
+Ou seja, temos um limite de estoque em fábrica para o primeiro dia deve ser de 30 unidades.
+
+Então estocando 30 unidades em fábrica no primeiro dia, e no segundo dia, como 10 unidades serão entregues para atender à demanda, teremos 20 unidades estocadas.
+
+No terceiro dia, mais 5 unidades serão entregues à demanda e o estoque ficará com 15 unidades.
+
+Já no quato dia, nada será entregue a demanda de forma que teremos um estoque de 15 unidades.
+Contudo o limite de estocagem para o quarto dia é de 10 unidades, assim teremos 5 unidades excedentes.
+Ou seja, é necessário que o estoque do primeiro dia seja reduzido em 5 unidades.
+
+A partir do raciocínio apresentado, podemos verificar a limitação do estoque em fábrica no primeiro dia deve levar em consideração às limitações de recebimento de estoque para cada dia seguinte, respeitando às retrições
+
+\begin{equation}
+	\textrm{UI}_{i} \leq UI_{i1}
+\end{equation}
+
+\begin{equation}
+	\textrm{UI}_{i} \leq UI_{id} + \sum_{k=2}^{d}\{\textrm{UD}_{ik} - D_{ik}\}
+\end{equation}
+
+Aqui temos, para o produto $p$:
+
+\begin{equation}
+	RL_{i1} \leq 40
+\end{equation}
+
+\begin{equation}
+	RL_{i2} \leq 20 + 10 , RL_{i2} \leq 30
+\end{equation}
+
+\begin{equation}
+	RL_{i3} \leq 15 + (10+5) , RL_{i3} \leq 30
+\end{equation}
+
+\begin{equation}
+	RL_{i4} \leq 10 + (10+5) , RL_{i4} \leq 25
+\end{equation}
+
+então temos que:
+
+\begin{equation}
+	\textrm{UI}_{i} = \min\{UI_{i1}, \min_d\{UI_{id} + \sum_{k=2}^{d}\{\textrm{UD}_{ik} - D_{ik}\}\}\}
+\end{equation}
+
+So, based on calculated values, we built the MPBPTM problem using the equations:
+
+\begin{equation}
+PL_id = UI_{i(d)} - UD_{i} \quad \forall i
+\end{equation}
+
+\begin{equation}
+\textrm{UD}_{i} = \textrm{UD}_{i1} - D_{i1} \quad \forall i
 \end{equation}
@@
 
-Sendo $\textrm{p}_{i}$ e $\textrm{Z}$ definidos de acordo com o problema apresentado.
+Being $\textrm{p}_{i}$ and $\textrm{Z}$ defined according to the MPMPBPTM problem presented. \\
 
-E resolvemos esse novo problema usando o método de partição do tempo proposto por Fraga (Fraga et al., 2023).\\
+Obs: Note that some values of $UI_{id}$ and  $I_{d}$ can be negative.
+This means that, in prior planning, some demand of the first day will be met by some previous planned production performed in a future period and that cannot be modified, i.e.
+$D_{id} > D_{id}^-$ for at least one ordained pair $(i,d)$.
+In this case, considering that prior planning was a viable planning, the negative values of the $UI_{id}$ and $I_{d}$ will be offset by the positive surplus values of $\textrm{UD}_{i}$, so this will not result in change in the optimal solution of the problem through the method used in the next step.
+\\
+
+The possible negative maximum values for variables are defined by the following equations. If this equations are not met, it means that initial planning was not a viable planning.
+
+\begin{equation}
+\max_d\{UI_{id}\} \geq \textrm{UD}_{i1} - D_{i1}, \quad \forall i
+\end{equation}
+
+\begin{equation}
+\max_d\{I_{d}\} \geq \sum_{i}\{ \textrm{UD}_{i1} - D_{i1} \}
+\end{equation}
+
+\emph{Step 3: MPBPTM solution by Fraga's analytical method} \\
+
+Once the MPBPTM problem is built, it can be solved by the analytical method proposed by Fraga (Fraga et al., 2023). This method can be resumed into two steps, as follows: \\
+
+step 1: find $T^*$, where:
+\begin{equation}
+T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
+\end{equation}
+
+step 2: calculate $T$, where:
+
+\begin{equation}
+T = \min \{T^* , \textrm{Z}\}
+\end{equation} \\
 

### 2023-08-04 multi-period/manuscript.tex
updating paper
UI_i and I calculation explanation
updating paper
explaining why later modification has no sense.

@@
 
-passo 1: Calcular a quantidade limite para estocagem em fábrica para cada produto, $\textrm{UI}_{i}$.
-
-\begin{equation}
-	\max \textrm{UI}_{i}
-\end{equation}
-
-\emph{sj. to}:
-
-\begin{equation}
-	\textrm{UI}_{i} \leq UI_{i1}
-\end{equation}
-
-\begin{equation}
-	\textrm{UI}_{i} \leq UI_{id} + \sum_{k=2}^{d}\{\textrm{UD}_{ik} - D_{ik}\}
-\end{equation}
-
-Para compreender a solução proposta, vamos considerar um exemplo:
-
-para 3 dias de planejamento, temos:
-
-dia --> estoque disponível --> demanda não atendida no dia --> soma da demanda não atendida
-
-d1 --> 40
-
-d2 --> 20 --> 10 --> 10
-
-d3 --> 15 --> 5 --> 15
-
-d4 --> 10 --> 0 --> 15
-
-considerando apenas o limite de estoque para o primeiro dia, a parcela da produção que pode ser estocada em fábrica é $40$.
-
-Contudo, esse estoque ficará em fábrica durante todo o período de planejamento considerado, exceto se houver saída para atender à demanda.
-
-Assim, no segundo dia o estoque será igual ao estoque do primeiro dia menos o valor que sairá para atender à demanda acumulada para o dia.
-
-o limite de recebimento de estoque do segundo dia será o limite de estoque mais a demanda não atendida.
-
-Então das 40 unidades estocadas em fábrica no primeiro dia, dez unidades serão entregues à demanda e 30 unidades ficarão estocadas em fábrica.
-
-Como o limite de estoque em fábrica para o segundo dia é de 20 unidades, então isso significa que há 10 unidades excedentes em estoque de fábrica.
-Ou seja, o estoque do primeiro dia, e portanto a produção devem ser diminuídos em 10 unidades.
-
-Ou seja, temos um limite de estoque em fábrica para o primeiro dia deve ser de 30 unidades.
-
-Então estocando 30 unidades em fábrica no primeiro dia, e no segundo dia, como 10 unidades serão entregues para atender à demanda, teremos 20 unidades estocadas.
-
-No terceiro dia, mais 5 unidades serão entregues à demanda e o estoque ficará com 15 unidades.
-
-Já no quato dia, nada será entregue a demanda de forma que teremos um estoque de 15 unidades.
-Contudo o limite de estocagem para o quarto dia é de 10 unidades, assim teremos 5 unidades excedentes.
-Ou seja, é necessário que o estoque do primeiro dia seja reduzido em 5 unidades.
-
-A partir do raciocínio apresentado, podemos verificar a limitação do estoque em fábrica no primeiro dia deve levar em consideração às limitações de recebimento de estoque para cada dia seguinte, respeitando às retrições
-
-\begin{equation}
-	\textrm{UI}_{i} \leq UI_{i1}
-\end{equation}
-
-\begin{equation}
-	\textrm{UI}_{i} \leq UI_{id} + \sum_{k=2}^{d}\{\textrm{UD}_{ik} - D_{ik}\}
-\end{equation}
-
-Aqui temos, para o produto $p$:
-
-\begin{equation}
-	RL_{i1} \leq 40
-\end{equation}
-
-\begin{equation}
-	RL_{i2} \leq 20 + 10 , RL_{i2} \leq 30
-\end{equation}
-
-\begin{equation}
-	RL_{i3} \leq 15 + (10+5) , RL_{i3} \leq 30
-\end{equation}
-
-\begin{equation}
-	RL_{i4} \leq 10 + (10+5) , RL_{i4} \leq 25
-\end{equation}
-
-então temos que:
-
-\begin{equation}
-	\textrm{UI}_{i} = \min\{UI_{i1}, \min_d\{UI_{id} + \sum_{k=2}^{d}\{\textrm{UD}_{ik} - D_{ik}\}\}\}
-\end{equation}
-
 So, based on calculated values, we built the MPBPTM problem using the equations:
-
-\begin{equation}
-PL_id = UI_{i(d)} - UD_{i} \quad \forall i
-\end{equation}
 
@@
 \begin{equation}
-\textrm{UI}_{i} = \min_{d} \{UI_{id}\}, \quad \forall{i}
+	\textrm{UI}_{i} = \min_d\{UI_{id}\}
 \end{equation}
@@
 
-$\textrm{P}_{11} = 1000$,
+$\textrm{P}_{11} = 800$,
 $\textrm{P}_{12} = 0$,
-$\textrm{P}_{21} = 0$,
-$\textrm{P}_{22} = 1500$. \\
+$\textrm{P}_{21} = 2,500$,
+$\textrm{P}_{22} = 1,500$. \\
 
@@
 
-$\textrm{UD}_{11} = 1000$,
+$\textrm{UD}_{11} = 1,000$,
 $\textrm{UD}_{12} = 500$,
@@
 
-$D_{11} = 1000$,
+$D_{11} = 800$,
 $D_{12} = 0$,
@@
 $UI_{22} = 2000 - 1500 + 300 + 600 =  1400$. \\
+
+$UI_{11} = 4,800 - 800 +  1000 = 4,000$
+$UI_{11} = 4,000 - 2,500 + 500 = 2,000$
+
+Na forma de distribuição planjeda - primeiro para atender demanda, depois para outlets e por último para estoque em fábrica... 
+no planejamento prévio, se eu reduzo o espeço disponível em estoque, do dia anterior para o dia em análise, é porque a produção extra foi suficiente para atender à toda demanda acumulada para o dia e também envio para outlet e sobrou produção para o estoque.
+Assim só e possível reduzir espaço disponível em estoque, se demanda acumulada não atendida for nula, assim como espaço disponível em outlets nulo para o produto.
+Portanto fórmula anterior (29) não carrega nenhum sentido.
+
+O mesmo pensamento pode ser considerado no caso do limite de estoque geral.
 

### 2023-08-04 multi-period/manuscript.tex
updating paper
undoing

@@
 \begin{equation}
-	\textrm{UI}_{i} = \min_d\{UI_{id}\}
+\textrm{UI}_{i} = \min_{d} \{UI_{id}\}, \quad \forall{i}
 \end{equation}
@@
 
-$\textrm{P}_{11} = 800$,
+$\textrm{P}_{11} = 1000$,
 $\textrm{P}_{12} = 0$,
-$\textrm{P}_{21} = 2,500$,
-$\textrm{P}_{22} = 1,500$. \\
+$\textrm{P}_{21} = 0$,
+$\textrm{P}_{22} = 1500$. \\
 
@@
 
-$\textrm{UD}_{11} = 1,000$,
+$\textrm{UD}_{11} = 1000$,
 $\textrm{UD}_{12} = 500$,
@@
 
-$D_{11} = 800$,
+$D_{11} = 1000$,
 $D_{12} = 0$,
@@
 $UI_{22} = 2000 - 1500 + 300 + 600 =  1400$. \\
-
-$UI_{11} = 4,800 - 800 +  1000 = 4,000$
-$UI_{11} = 4,000 - 2,500 + 500 = 2,000$
-
-Na forma de distribuição planjeda - primeiro para atender demanda, depois para outlets e por último para estoque em fábrica... 
-no planejamento prévio, se eu reduzo o espeço disponível em estoque, do dia anterior para o dia em análise, é porque a produção extra foi suficiente para atender à toda demanda acumulada para o dia e também envio para outlet e sobrou produção para o estoque.
-Assim só e possível reduzir espaço disponível em estoque, se demanda acumulada não atendida for nula, assim como espaço disponível em outlets nulo para o produto.
-Portanto fórmula anterior (29) não carrega nenhum sentido.
-
-O mesmo pensamento pode ser considerado no caso do limite de estoque geral.
 

### 2023-08-09 blindedManuscrip1t.tex
before changes
improving model for considering priorities

--- 2023-07-27 manuscript.tex
@@
 
-\documentclass[authoryear,preprint,12pt]{elsarticle}
+\documentclass[authoryear,manuscript,12pt]{elsarticle}
+\usepackage{setspace}
+\doublespacing
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{lemma}[theorem]{Lemma}
 
@@
 
-\journal{Applied Mathematical Modelling}
+\journal{Computers \& Industrial Engineering}
 
@@
 %%             country={}}
-
-%\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}
-
-\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
-\ead{tatiana.balbi@ufpe.br}
-\cortext[cor1]{corresponding author}
-
-\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
-\ead{italo_ruan_@hotmail.com}
-
-\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
-\ead{regilda.smenezes@ufpe.br}
-
 %\affiliation[label1]{
@@
 The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch.
-In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem.
+In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem.
 We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
@@
 \item brief bibliographic review on multi-product batch problems;
-\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
-\item linear integer programming model for the MPBPTM problem;
-\item exact optimization method for solving the MPBPTM problem.
+\item Multi-product Batch Processing Time Maximization (MBPTM) problem definition;
+\item linear integer programming model for the MBPTM problem;
+\item exact optimization method for solving the MBPTM problem.
 \end{highlights}
@@
 
-Given that: \\
+Given that:
 
@@
 
-$T$ is the batch processing time. \\
+$T$ is the batch processing time.
 
-We have the problem: \\
+We have the problem:
 
 \begin{equation}
+\label{MBPTMP01}
 max \quad T
@@
 \begin{equation}
+\label{MBPTMP04}
 D_i \leq \textrm{UD}_i \quad \forall i
@@
 \begin{equation}
+\label{MBPTMP10}
 T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
@@
 
-where: \\
+where:
 
@@
 
-where $E_i$ is the sum of the quantity stored at the factory and the quantity sent to the outlets of the product $i$. \\
+where $E_i$ is the sum of the quantity stored at the factory and the quantity sent to the outlets of the product $i$.
 
@@
 
-In this case, we can find $T'''$ by solving the second reduced problem:
+In this case, we can find $T''$ by solving the second reduced problem:
 
@@
 \begin{equation}
-\sum_i {E_i - S_i} \leq \textrm{O} + \textrm{I}
+\sum_i ({E_i - S_i}) \leq \textrm{O} + \textrm{I}
 \end{equation}
@@
 So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.
-\\
 
-So, the analytical method can be decomposed into 4 steps: \\
+So, the analytical method can be decomposed into 4 steps:
 
@@
 
-It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper. \\
+Note that there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
+Thus it is possible to use a simplification of the method presented, making $T' = 0$.
+In this case $S_i = \textrm{UD}_i, \forall i$.
+The simplified version of the method is presented below:
 
-\emph{Solution for the example presented before} \\
+step 1: find $T^*$, where:
+\begin{equation}
+T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
+\end{equation}
 
-Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\
-
-$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T' \leq 16 \textrm{ min}$ \quad for A \\
-
-$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T' \leq 12 \textrm{ min}$ \quad for B \\
-
-so: \\
-
-$T' = 12 \textrm{ min}$ \\
-
-Then:\\
-
-$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$ \\
-
-$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$ \\
-
-And so we have: \\
-
-$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 64 \textrm{ min}$ \quad for A \\
-
-$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 65 \textrm{ min}$ \quad for B \\
-
-$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 43 \textrm{ min}$ \quad for A and B \\
-
-So that: \\
-
-$T'' = 43 \textrm{ min}$ \\
-
-So we have: \\
-
-$T = 55 \textrm{ min}$ \\
-
-As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution. \\
-
-In this case we will have: \\
-
-$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$ \\
-
-$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$ \\
-
-$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$ \\
-
-Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the undetermined system of inequalities:
+step 2: calculate $T$, where:
 
 \begin{equation}
-O_i + I_i = E_i \quad \forall i
+T = \min \{T^* , \textrm{Z}\}
+\end{equation}
+
+It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper.
+
+\emph{Solution for the example presented before}
+
+Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have:
+
+$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$
+
+$T' \leq 16 \textrm{ min}$ \quad for A
+
+$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$
+
+$T' \leq 12 \textrm{ min}$ \quad for B
+
+so:
+
+$T' = 12 \textrm{ min}$
+
+Then:
+
+$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$
+
+$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$
+
+And so we have:
+
+$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$
+
+$T'' \leq 64 \textrm{ min}$ \quad for A
+
+$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$
+
+$T'' \leq 65 \textrm{ min}$ \quad for B
+
+$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$
+
+$T'' \leq 43 \textrm{ min}$ \quad for A and B
+
+So that:
+
+$T'' = 43 \textrm{ min}$
+
+So we have:
+
+$T = 55 \textrm{ min}$
+
+As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution.
+
+In this case we will have:
+
+$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$
+
+$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$
+
+$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$
+
+Observe that $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory.
+However, after determining a solution, the values of $D_i$, $O_i$ and $I_i$, $\forall i$, can be found by taking a solution from the undetermined system of inequalities:
+
+\begin{equation}
+D_i + O_i + I_i = P_i \quad \forall i
+\end{equation}
+
+\begin{equation}
+D_i \leq \textrm{UD}_i \quad \forall i
 \end{equation}
@@
 \begin{equation}
+\label{eq:resO}
 \sum_i{O_i} \leq \textrm{O}
@@
 \begin{equation}
+\label{eq:resI}
 \sum_i{I_i} \leq \textrm{I}
@@
 \begin{equation}
-O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
+D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
 \end{equation}
+
+It seems natural that every industry has as a priority to meet demand and that it is preferable to send the remaining production to outlets rather then stock it in the factory.
+Therefore, we can determine the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by defining these priorities for distribution.
+The following three algorithms can be used to find a complete solution:
+
+\begin{algorithm}
+\caption{Solving MBPTMP | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
+\begin{algorithmic}
+	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
+	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
+	\State $T \gets \min \{T^* , \textrm{Z}\}$
+\State \textbf{Return:} $T$.
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Solving MBPTMP | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions in (\ref{eq:resO}) and (\ref{eq:resI}).}\label{alg:part02}
+\begin{algorithmic}
+	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
+	\For{all i}
+		\State $E_i \gets T * \textrm{p}_i$
+		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
+		\State $E_i \gets E_i - D_i$
+		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
+		\State $E_i = E_i - O_i$
+		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
+		\State $I_i = E_i$
+		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
+	\EndFor
+	\State $SO = \textrm{O} - \sum_i{O_i}$
+	\State $SI = \textrm{I} - \sum_i{I_i}$
+	\State \textbf{Return:} $D_i, O_i, I_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
+\end{algorithmic}
+\end{algorithm}
+
+After applying algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
+However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
+But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:
+
+\begin{lemma}
+Let \(T\) be a optimal solution to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}) and $SO$ and $SI$ defined by algorithm (\ref{alg:part02}), so: \\
+
+$if \quad SO < 0 \quad then \quad SI > 0 \quad and  \quad |SO| < SI$
+
+$if \quad SI < 0 \quad then \quad SO > 0 \quad and  \quad |SI| < SO$
+
+\end{lemma}
+
+Therefore it is possible to meet the restrictions in (\ref{eq:resO}) and (\ref{eq:resI}) by applying the agorithm (\ref{alg:part03}).
+
+\begin{algorithm}
+\caption{Solving MBPTMP | Part 03: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part03}
+\begin{algorithmic}
+\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
+\If{$SO < 0$}
+\For{all $i$}
+	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
+	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
+	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
+	\If{$SO = 0$}
+		break looping for;
+	\EndIf
+\EndFor
+\EndIf
+
+\If{$SI < 0$}
+\For{all $i$}
+	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
+	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
+	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
+	\If{$SI = 0$}
+		break looping for;
+	\EndIf
+\EndFor
+\EndIf
+\State \textbf{Return:} $O_i, I_i, \forall i$.
+\end{algorithmic}
+\end{algorithm}
+
+\emph{Solution for the example presented before - determining the values of $D_i$, $O_i$ and $I_i$, $\forall i$.}
+
+$T = 55 \textrm{min}$
+
+$E_A = 55 \textrm{min}* 60 \textrm{ g}/\textrm{min}  = 3,300 \textrm{ g}$
+
+$E_B = 55 \textrm{min}* 40 \textrm{ g}/\textrm{min}  = 2,200 \textrm{ g}$
+
+$D_A = \min \{1,000 \textrm{ g}, \textrm{ } 3,300 \textrm{ g}\} = 1,000 \textrm{ g} $
+
+$D_B = \min \{500 \textrm{ g}, \textrm{ } 2,200 \textrm{ g}\} = 500 \textrm{ g} $
+
+$E_A = 3,300 \textrm{ g} - 1,000 \textrm{ g} = 2,300 \textrm{ g}$
+
+$E_B = 2,200 \textrm{ g} - 500 \textrm{ g} = 1,700 \textrm{ g}$
+
+$O_A = \min \{600 \textrm{ g}, \textrm{ }  2,000 \textrm{ g}\} = 600 \textrm{ g}$
+
+$O_B = \min \{600 \textrm{ g}, \textrm{ }  1,700 \textrm{ g}\} = 600 \textrm{ g}$
+
+$E_A = 2,300 \textrm{ g} - 600 \textrm{ g} = 1,700 \textrm{ g}$
+
+$E_B = 1,700 \textrm{ g} - 600 \textrm{ g} = 1,100 \textrm{ g}$
+
+$\textrm{UO}_A = 600 \textrm{ g} - 600 \textrm{ g} = 0 \textrm{ g}$
+
+$\textrm{UO}_B = 600 \textrm{ g} - 600 \textrm{ g} = 0 \textrm{ g}$
+
+$I_A = 1,700 \textrm{ g}$
+
+$I_B = 1,100 \textrm{ g}$
+
+$\textrm{UI}_A = 3,000 \textrm{ g} - 1,700 \textrm{ g} = 1,300 \textrm{ g}$
+
+$\textrm{UI}_B = 2,000 \textrm{ g} - 1,100 \textrm{ g} = 900 \textrm{ g}$
+
+$SO = 1,000 \textrm{ g} - 1,200 \textrm{ g} = - 200 \textrm{ g}$
+
+$SI = 3,000 \textrm{ g} - 2,800 \textrm{ g} = 200 \textrm{ g}$
+
+\emph{Redistribution}
+
+$O_A = 600 \textrm{ g} - \min \{600 \textrm{ g}, \textrm{ }  1,300 \textrm{ g}, \textrm{ }  200 \textrm{ g}\} = 400 \textrm{ g}$
+
+$I_A = 1,700 \textrm{ g} + \min \{600 \textrm{ g}, \textrm{ }  1,300 \textrm{ g}, \textrm{ }  200 \textrm{ g}\} = 1,900 \textrm{ g}$
+
+$SO = 200 \textrm{ g} + \min \{600 \textrm{ g}, \textrm{ }  1,300 \textrm{ g}, \textrm{ }  200 \textrm{ g}\} = 0 \textrm{ g}$
+
+\emph{Solution}
+
+$T = 55 \textrm{min}; \quad D_A = 1,000 \textrm{ g}; \quad D_B = 500 \textrm{ g}; \quad O_A = 400 \textrm{ g}; \quad O_B = 600 \textrm{ g}; \quad I_A = 1,900 \textrm{ g}; \quad \textrm{and } I_B = 1,100 \textrm{ g}$.
 
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (https://github.com/tbfraga/COPSolver).
+To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (https://github.com/blinded).
 The tests were performed on a notebook with an Intel i7 processor.
@@
 
-T.B.
-Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
-Í.R.B.
-Aquino: Data curation.
-R.C.S.
-Menêzes: Data curation.
+Blinded, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing. Blinded: Data curation. Blinded: Data curation.
 
@@
 
-We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects.
-We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process.
-Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects.
-We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.
+Blinded
 

### 2023-08-09 titlePage.tex
before changes
improving model for considering priorities

--- 2023-07-27 manuscript.tex
@@
 %%Graphical abstract
-\begin{graphicalabstract}
-\includegraphics[width=0.8\textwidth]{graphical.png}
-\end{graphicalabstract}
+%\begin{graphicalabstract}
+%\end{graphicalabstract}
 
 %%Research highlights
-\begin{highlights}
-\item brief bibliographic review on multi-product batch problems;
-\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
-\item linear integer programming model for the MPBPTM problem;
-\item exact optimization method for solving the MPBPTM problem.
-\end{highlights}
+%\begin{highlights}
+%\end{highlights}
 
@@
 %% main text
-\section{Introduction}
-\label{sec:intro}
-
-The scientific literature presents several papers that address multi-product batch problems.
-Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}.
-In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed.
-The solution must be determined in such a way that both setup and storage costs are minimized.
-Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}.
-\cite{MendezEtAll2000} and \cite{ShiEtAll2017} present two parallel multi-product batch scheduling (PMPBS) problems, in which production units of the same type are arranged in parallel, forming each production stage.
-In this case, it is also necessary to define in which units each product will be processed.
-The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance).
-In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages.
-\cite{KimEtAl1996} consider the multi-product batch problem in networked processes.
-As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist.
-Therefore, the production paths in the flowshop network can be different for each product.
-Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence.
-In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time.
-\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints.
-In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine.
-However, there are no production limitations for the production of each product group.
-The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems.
-Other important works deal with the problem of a multi-product batch plant design (MPBPD).
-In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).
-
-In this work, we are concerned with determining the ideal processing time for a single batch consisting of a set of products, each product being or not different from the other products of the same batch.
-That is, we consider a specific case where different products are processed simultaneously on the same processor.
-This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.
-
-As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.
-
-In the next sections, a presentation of problem is made along with an application example.
-Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution.
-Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks.
-In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions to this work are informed and acknowledgments are given, respectively.
-Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.
-
-\section{Multi-product batch processing time maximization problem}
-\label{sec:MBPTMP}
-
-The multi-product batch processing time maximization problem arises when a set of different products are processed simultaneously in a same production batch.
-In this problem, it is considered that the quantity produced of each product is directly proportional to the processing time, however, with a different constant of proportionality (production rate) for each product.
-In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
-The maximum production quantity of each product is mainly defined according to the demand for the product.
-However, it is still possible to stock the products and/or send them to the outlets.
-In both cases, there is a stocking/shipping limit for each product and a stocking/shipping limit for the set of products in the batch.
-Also, there is a time limit available for processing the batch.
-The problem consists of defining the maximum processing time for the batch, respecting the limitations related to the quantities produced.
-For a better understanding of the problem, an example is presented below.
-
-\emph{Example:} A certain machine must process a batch containing 2 different products: A and B.
-The production rate of A is 60 g/min while the production rate of B is 40 g/min.
-The factory has free stock for a maximum of 3000 g of any product, and, according to the company's inventory policy, a maximum of 3000 g of product A and 2000 g of product B can be stocked at the factory.
-There is a demand for 1000 g of product A and 500 g of product B.
-The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product.
-A maximum time of 100 minutes of this machine can be allocated for processing this batch.
-What is the maximum possible time for processing this batch ?
-
-\section{Mathematical model}
-\label{sec:mathModel}
-
-Given that: \\
-
-$\textrm{UD}_i$ is the demand for the product $i$;
-
-$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;
-
-$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;
-
-$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;
-
-$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;
-
-$\textrm{p}_i$ is the production rate of product $i$;
-
-$\textrm{Z}$ is the timeout for batch processing;
-
-$P_i$ is the amount of product $i$ produced;
-
-$D_i$ is the amount of product $i$ delivered for the demand;
-
-$O_i$ amount of product $i$ shipped to factory outlets;
-
-$I_i$ is the amount of product $i$ that will be stored at the factory;
-
-$T$ is the batch processing time. \\
-
-We have the problem: \\
-
-\begin{equation}
-max \quad T
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-P_i - \textrm{p}_i * T  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-P_i - D_i - O_i - I_i = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{O_i} \leq \textrm{O}
-\end{equation}
-
-\begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{I_i} \leq \textrm{I}
-\end{equation}
-
-\begin{equation}
-T \leq \textrm{Z}
-\end{equation}
-
-\begin{equation}
-T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-where: \\
-
-Constraints in (2) relate the quantity produced, $P_i$, to batch processing time $T$.
-Constraints in (3) calculate the quantity produced, $P_i$, as a function of the primary variables, $D_i$, $O_i$ and $I_i$.
-Constraints in (4), (5), and (7) state that the quantity delivered to demand, the quantity shipped to the autlets, and the factory-stocked quantity of each product must be less than their respective known limits.
-Constraints (6) and (8) state that both the sum of product quantities sent to the autlets and the sum of product quantities stocked in the factory must be less than their respective maximum allowed values.
-The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
-And finally, the constraints in (10) inform the nature of the decision variables.
-
-\section{Analytical solution}
-\label{sec:analyticalSol}
-
-It is possible to consider the factory stock and the outlets stock as single stock, so we have:
-
-\begin{equation}
-E_i = O_i + I_i
-\end{equation}
-
-where $E_i$ is the sum of the quantity stored at the factory and the quantity sent to the outlets of the product $i$. \\
-
-So that:
-
-\begin{equation}
-E_i \leq \textrm{UO}_i + \textrm{UI}_i
-\end{equation}
-
-and
-
-\begin{equation}
-\sum_i {E_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-It is also possible to split the batch processing time into two time slots:
-
-\begin{equation}
-T = T' + T''
-\end{equation}
-
-and consider that $T'$ is the maximum processing time used only for production that will meet the demand. Thus, we can find $T'$, solving the reduced problem:
-
-\begin{equation}
-max \quad T'
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-D_i - \textrm{p}_i * T'  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i, T' \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-This reduced problem can be rewritten in the form:
-
-\begin{equation}
-max \quad T'
-\end{equation}
-
-$s.t.$ \\
-
-\begin{equation}
-T'  \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
-\end{equation}
-
-So we have that $T'$ will be the smallest of the ratios $\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor$ of all products. \\
-
-Once we find the value of $T'$, we can calculate the value of unmet demand for each product after $T'$, $S_i$, through the equations in (\ref{eq:unmet1}).
-
-\begin{equation}
-\label{eq:unmet1}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-Now we consider that the time interval $T''$ will be used for the production of the quantities that will be stored (in the factory and in the outlets), as well as of the demand not met by the production in the first time interval, $S_i$.
-
-In this case, we can find $T'''$ by solving the second reduced problem:
-
-\begin{equation}
-max \quad T''
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-E_i - \textrm{p}_i * T''  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-E_i - S_i \leq \textrm{UO}_i + \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i {E_i - S_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-\begin{equation}
-E_i, T'' \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-Again, using a little algebra, we can rewrite this reduced problem in the form:
-
-\begin{equation}
-max \quad T''
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-T'' \leq \lfloor{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i}\rfloor  \quad \forall i
-\end{equation}
-
-\begin{equation}
-T'' \leq \lfloor{(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}}\rfloor
-\end{equation}
-
-So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.
-\\
-
-So, the analytical method can be decomposed into 4 steps: \\
-
-step 1: find $T'$, where:
-\begin{equation}
-T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
-\end{equation}
-
-step 2: calculate $S_i$ for all products.
-\begin{equation}
-\label{eq:unmet}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-step 3: find $T''$, where:
-\begin{equation}
-T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 4: calculate $T$, where: 
-\begin{equation}
-T = T' + T''
-\end{equation}
-\begin{equation}
-T = \min \{T , \textrm{Z}\}
-\end{equation}
-
-It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper. \\
-
-\emph{Solution for the example presented before} \\
-
-Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\
-
-$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T' \leq 16 \textrm{ min}$ \quad for A \\
-
-$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T' \leq 12 \textrm{ min}$ \quad for B \\
-
-so: \\
-
-$T' = 12 \textrm{ min}$ \\
-
-Then:\\
-
-$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$ \\
-
-$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$ \\
-
-And so we have: \\
-
-$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 64 \textrm{ min}$ \quad for A \\
-
-$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 65 \textrm{ min}$ \quad for B \\
-
-$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 43 \textrm{ min}$ \quad for A and B \\
-
-So that: \\
-
-$T'' = 43 \textrm{ min}$ \\
-
-So we have: \\
-
-$T = 55 \textrm{ min}$ \\
-
-As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution. \\
-
-In this case we will have: \\
-
-$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$ \\
-
-$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$ \\
-
-$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$ \\
-
-Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining a solution, these values can be found by taking a solution from the undetermined system of inequalities:
-
-\begin{equation}
-O_i + I_i = E_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{O_i} \leq \textrm{O}
-\end{equation}
-
-\begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i{I_i} \leq \textrm{I}
-\end{equation}
-
-\begin{equation}
-O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-\section{Tests and results}
-\label{sec:results}
-
-To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (https://github.com/tbfraga/COPSolver).
-The tests were performed on a notebook with an Intel i7 processor.
-We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\
-
-\begin{equation}
-\textrm{p}_i = \textrm{rand}()\%30 + 10
-\end{equation}
-
-\begin{equation}
-\textrm{UD}_i = \textrm{rand}()\%3000 + 800;
-\end{equation}
-
-\begin{equation}
- \textrm{seed1} = \textrm{rand}()\%3000 + 500;
-\end{equation}
-
-\begin{equation}
-\textrm{seed2} = \textrm{rand}()\%5000 + 1000;
-\end{equation}
-
-\begin{equation}
-\textrm{O} = \textrm{N}/2*\textrm{seed1};
-\end{equation}
-
-\begin{equation}
-\textrm{UO}_i = \textrm{rand}()\%(\textrm{seed1}-500) + 500;
-\end{equation}
-
-\begin{equation}
-\textrm{I} = \textrm{N}/2*\textrm{seed2};
-\end{equation}
-
-\begin{equation}
-\textrm{UI}_i = \textrm{rand}()\%(\textrm{seed2}-1000) + 1000;
-\end{equation}
-
-\begin{equation}
-\textrm{Z} = 100;
-\end{equation}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r}
-$i$ & 1 & 2 & total \\
-\cline {1-4} \\
-$\textrm{p}_i$ & 60 & 40 & \\
-$\textrm{UD}_i$ & 1000 & 500 & \\
-$\textrm{UO}_i$ & 600 & 600 & 1000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 3000 \\
-\cline {1-4} \\
-& & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MPBPTMP 001}
-\label{tab:MBPTMP001}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}[c]{c r r r r}
-$i$ & 1 & 2 & 3 & total \\
-\cline {1-5} \\
-$\textrm{p}_i$ & 60 & 40 & 50 \\
-$\textrm{UD}_i$ & 1000 & 500 & 800 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 3500 \\
-\cline {1-5} \\
-& & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MPBPTMP 002}
-\label{tab:MBPTMP002}
-\end{center}
-\end{table}
-
-\begin{table}[h]
-\begin{center}
-\begin{small}
-\begin{tabular}[c]{c r r r r r r r r r r r }
-$i$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & total \\
-\cline {1-12} \\
-$\textrm{p}_i$ & 60 & 40 & 50 & 40 & 30 & 50 & 60 & 10 & 20 & 40\\
-$\textrm{UD}_i$ & 1000 & 500 & 800 & 500 & 400 & 500 & 2000 & 300 & 500 & 1000 \\
-$\textrm{UO}_i$ & 600 & 600 & 600 & 1500 & 300 & 200 & 500 & 800 & 0 & 200 & 3000 \\
-$\textrm{UI}_i$ & 3000 & 2000 & 1000 & 800 & 3000 & 1000 & 400 & 300 & 200 & 0 & 5000 \\
-\cline {1-12} \\
-& & & & & & & & & & $\textrm{Z}$ & 100 \\
-\end{tabular}
-\caption{Benchmark MPBPTMP 003}
-\label{tab:MBPTMP003}
-\end{small}
-\end{center}
-\end{table}
-
-Randomly generated benchmarks were named RMPBPTMP $\textrm{N}$, being $\textrm{N}$ the number of products.
-Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
-To build the results presented in this work, we used source=0.
-The benchmarks used for the tests performed can be consulted at github.com/blinded.
-
-Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks.
-
-\begin{table}[h]
-\begin{center}
-\begin{footnotesize}
-\begin{tabular}[c]{l r r r r}
-problem & LINGO solver & time (s) & analytical method & time (s) \\
-\cline {1-5} \\
-MPBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
-MPBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
-MPBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
-RMPBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
-RMPBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
-RMPBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
-RMPBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
-RMPBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
-\cline {1-5} \\
-\end{tabular}
-\caption{Results obtained with the LINGO solver and the analytical method}
-\label{tab:results}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method.
-As the analytical method is a polynomial time complexity method, we did not intend to compare computational costs, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.
-
-We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi-period problem and try to propose new solution methods if needed.
-
-\section{Conclusions and suggestions for future works}
-\label{sec:conclusions}
-
-In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an analytical solution method for this problem.
-The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.
-Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method.
-As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem in a multi-period scenario.
-We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
-
-\section{CRediT authorship contribution statement} 
-\label{sec:contributions}
-
-T.B.
-Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
-Í.R.B.
-Aquino: Data curation.
-R.C.S.
-Menêzes: Data curation.
 
@@
 %% TeX file.
-
-\begin{thebibliography}{1}
-
-%% \bibitem[Author(year)]{label}
-%% Text of bibliographic item
-
-\bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
-Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt Sci.}, Vol. 13 (5), pp. 453--468.
-
-\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
-Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.
-
-\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
-Li, C., Wang, F., Gupta, J.N.D., Chung, T.
-(2022).
-Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints.
-{\it Computers \& Industrial Engineering}, Vol.
-169, pp.
-108115.
-
-\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
-Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.
-
-\bibitem[\protect\citeauthoryear{Méndez \emph{et al.}}{2000}]{MendezEtAll2000}
-Méndez, C.A., Henning, G.P., Cerdá, J. (2000). Optimal scheduling of batch plants satisfying multiple product
-orders with different due-dates. {\it Computers and Chemical Engineering}, Vol. 24, pp. 2223--2245.
-
-\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
-OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.
-
-\bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}
-Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.
-
-\bibitem[\protect\citeauthoryear{Shi \emph{et al.}}{2017}]{ShiEtAll2017}
-Shi, B., Qian, X., Sun, S., Yan, L. (2017). Rule-based scheduling of multi-stage multi-product batch plants with parallel units. {\it Chinese Journal of Chemical Engineering}, in press.
-
-\end{thebibliography}
 \end{document}

### 2023-08-09 manuscript.tex
updating paper
modifying math model

@@
 
-$T$ is the batch processing time. \\
+$T$ is the batch processing time;
 
-We have the problem: \\
+We have the problem:
+
+$UD_i - O_i$ e $O_i - UD_i$
 
 \begin{equation}
+\label{MBPTMP01}
 max \quad T
@@
 \begin{equation}
+\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0
+\end{equation}
+
+\begin{equation}
+\min\{\textrm{O} - \sum_i\{ O_i\}, \max\{0, I_i - O_i\}\} = 0
+\end{equation}
+
+\begin{equation}
+\label{MBPTMP10}
 T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i

### 2023-08-09 manuscript.tex
updating paper
changing math model

@@
 Also, there is a time limit available for processing the batch.
-The problem consists of defining the maximum processing time for the batch, respecting the limitations related to the quantities produced.
-For a better understanding of the problem, an example is presented below.
+About the production, the industry manager has as priority to meet demand and he prefer to send the remaining production to outlets rather then stock it in the factory.
 
@@
 A maximum time of 100 minutes of this machine can be allocated for processing this batch.
-What is the maximum possible time for processing this batch ?
+When distributing production the priority is to meet demand, then send to outlets and finily stock in factory.
+What is the maximum possible time for processing this batch and how production must be distributed ?
 
@@
 We have the problem:
-
-$UD_i - O_i$ e $O_i - UD_i$
 
@@
 \begin{equation}
-\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0
+\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
 \end{equation}
@@
 \begin{equation}
-\min\{\textrm{O} - \sum_i\{ O_i\}, \max\{0, I_i - O_i\}\} = 0
+\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
 \end{equation}
@@
 The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
-And finally, the constraints in (10) inform the nature of the decision variables.
+As equações em (10) e (11) definem a prioridade de distribuição da produção.
+And finally, the constraints in (12) inform the nature of the decision variables.
 
@@
 
-It is possible to consider the factory stock and the outlets stock as single stock, so we have:
+To solve the MBPTM problem we will start considering that, despite equations in (10) and (11) define a priority for production distribution, $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory.
+So we can find $T$, by ignoring this equations and, after finding $T$ for the relaxed model, use this eqautions for distribute the production based on the defined priorities.
+
+Then, it is possible to consider the factory stock and the outlets stock as single stock, so we have:
 
@@
 
-Observe that $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory.
-However, after determining a solution, the values of $D_i$, $O_i$ and $I_i$, $\forall i$, can be found by taking a solution from the undetermined system of inequalities:
+After determining a solution, the values of $D_i$, $O_i$ and $I_i$, $\forall i$, can be found by taking a solution from the undetermined system of inequalities:
 
@@
 \begin{equation}
+\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
 D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
@@
 
-It seems natural that every industry has as a priority to meet demand and that it is preferable to send the remaining production to outlets rather then stock it in the factory.
-Therefore, we can determine the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by defining these priorities for distribution.
-The following three algorithms can be used to find a complete solution:
+We can solve this system and determine the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by defining the priorities for distribution.
+The following three algorithms can be used to find a complete solution.
+
+The algorithm (\ref{alg:part01}) is used for finding an optimimal value fot $T$.
 
@@
 \end{algorithm}
+
+Then an initial production distribution can be done by the algorithm (\ref{alg:part02}).
 
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (https://github.com/tbfraga/COPSolver).
+To test the developed model and analytical solution method, we created a solver in C++ (COPSolver, V01\_20230809) and a solver in LINGO (https://github.com/tbfraga/COPSolver).
 The tests were performed on a notebook with an Intel i7 processor.
@@
 \end{tabular}
-\caption{Benchmark MPBPTMP 001}
+\caption{Benchmark MBPTM 2}
 \label{tab:MBPTMP001}
@@
 \end{tabular}
-\caption{Benchmark MPBPTMP 002}
+\caption{Benchmark MBPTM 3}
 \label{tab:MBPTMP002}
@@
 \end{tabular}
-\caption{Benchmark MPBPTMP 003}
+\caption{Benchmark MBPTM 10}
 \label{tab:MBPTMP003}
@@
 
-Randomly generated benchmarks were named RMPBPTMP $\textrm{N}$, being $\textrm{N}$ the number of products.
+Randomly generated benchmarks were named RMBPTM $\textrm{N}$, being $\textrm{N}$ the number of products.
 Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value.
@@
 \cline {1-5} \\
-MPBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
-MPBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
-MPBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
-RMPBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
-RMPBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
-RMPBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
-RMPBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
-RMPBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
+MBPTM 2 & 55 & 0.04 & 55 & 0.001 \\
+MBPTM 3 & 48 & 0.06 & 48 & 0.001 \\
+MBPTM 10 & 30 & 0.09 & 30 & 0.001 \\
+RMBPTM 20 & 100 & 0.08 & 100 & 0.001 \\
+RMBPTM 50 & 98 & 0.12 & 98 & 0.001\\
+RMBPTM 100 & 98 & 0.12 & 98 & 0.002\\
+RMBPTM 1,000 & 78 & 3.10 & 78 & 0.002\\
+RMBPTM 10,000 & 70 & 168.87 & 70 & 0.006 \\
 \cline {1-5} \\
@@
 \label{tab:results}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
+Files containing all results can be found at github.com/blinded.
+
+\begin{table}[h]
+\begin{center}
+\begin{footnotesize}
+\begin{tabular}[c]{l r r r r}
+product & production & delivered (s) & send to outlets & stocked in factory \\
+\cline {1-5} \\
+P1 & 2,880 & 1,000 & 300 & 1,580 \\
+P2 & 1,920 & 500 & 600 & 820 \\
+P3 & 2,400 & 800 & 600 & 1,000 \\
+\cline {1-5} \\
+\end{tabular}
+\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 3}
+\label{tab:compResultsMBPTMP2}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+\begin{table}[h]
+\begin{center}
+\begin{footnotesize}
+\begin{tabular}[c]{l r r r r}
+product & production & delivered (s) & send to outlets & stocked in factory \\
+\cline {1-5} \\
+P1 & 1,800 & 1,000 & 400 & 400 \\
+P2 & 1,200 & 500 & 600 & 100 \\
+P3 & 1,500 & 800 & 600 & 100 \\
+P4 & 1,200 & 500 & 700 & 0 \\
+P5 & 900 & 400 & 300 & 200 \\
+P6 & 1,500 & 500 & 200 & 800 \\
+P7 & 1,800 & 1800 & 0 & 0 \\
+P8 & 300 & 300 & 0 & 0 \\
+P9 & 600 & 500 & 0 & 100 \\
+P10 & 1,200 & 1000 & 200 & 0 \\
+\cline {1-5} \\
+\end{tabular}
+\caption{Results obtained with the LINGO solver and COPSolver for the MBPTM 10}
+\label{tab:compResultsMBPTMP3}
 \end{footnotesize}

### 2023-08-09 manuscript.tex
updating paper
improving math model to include production distribution priorities

@@
 
-To test the developed model and analytical solution method, we created a solver in C++ (COPSolver, V01\_20230809) and a solver in LINGO (https://github.com/tbfraga/COPSolver).
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230809, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MPBPTM.lng both available at https://github.com/tbfraga/COPSolver.
 The tests were performed on a notebook with an Intel i7 processor.
@@
 
-Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks.
+Table \ref{tab:results} presents the results obtained by applying the analytical method (COPSolver) and the LINGO solver for the solution of the previously presented benchmarks.
 
@@
 Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
-Files containing all results can be found at github.com/blinded.
+Files containing all results can be found at github.com/tbfraga/COPSolver.
 
@@
 
-In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an analytical solution method for this problem.
+In this paper we presented the Multi-product Batch Processing Time Maximization problem, as well as a mathematical model and an exact analytical solution method for this problem.
 The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO software, from LINDO Systems, and with a solver developed in C++ language.

### 2023-08-14 manuscript.tex
updating manuscript

@@
 In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MBPTM) problem.
-We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
+We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
 \end{abstract}
@@
 \begin{keyword}
-multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
+multiproduct batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep LINGO
 \end{keyword}
@@
 \label{sec:intro}
+
+Starting a working day... 
+Tasks finish tests using LINGO on optimization mode.
+Submit paper again to journal.
 
@@
 
-As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MPBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.
+As scientific contributions, in this paper we define a new multi-product batch problem, named multi-product batch processing time maximization (MBPTM) problem, as well as a mathematical model and a polynomial time complexity analytical solution optmization method for solving this problem.
 
@@
 In addition, there is a maximum quantity allowed for the production of batch products, defined both individually and for the set.
-The maximum production quantity of each product is mainly defined according to the demand for the product.
+The production quantity of each product is mainly defined according to the demand for the product.
 However, it is still possible to stock the products and/or send them to the outlets.
@@
 The restriction in (9) establishes that there is a batch processing time limit, $\textrm{Z}$, that must be respected.
-As equações em (10) e (11) definem a prioridade de distribuição da produção.
+Equations in (10) and (11) define the production distribution priority.
 And finally, the constraints in (12) inform the nature of the decision variables.
@@
 To solve the MBPTM problem we will start considering that, despite equations in (10) and (11) define a priority for production distribution, $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory.
-So we can find $T$, by ignoring this equations and, after finding $T$ for the relaxed model, use this eqautions for distribute the production based on the defined priorities.
+So we can find $T$, by ignoring this equations and, after finding $T$ for the relaxed model, solving the production distribution problem based on the defined priorities.
 
-Then, it is possible to consider the factory stock and the outlets stock as single stock, so we have:
+After relaxation of the problem, it is possible to consider the factory stock and the outlets stock as single stock, so we have:
 
@@
 \begin{equation}
-D_i + O_i + I_i = P_i \quad \forall i
+D_i + O_i + I_i = p_i*T \quad \forall i
 \end{equation}
@@
 To build the results presented in this work, we used source=0.
-The benchmarks used for the tests performed can be consulted at github.com/blinded.
+The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.
 
@@
 MBPTM 10 & 30 & 0.09 & 30 & 0.001 \\
-RMBPTM 20 & 100 & 0.08 & 100 & 0.001 \\
-RMBPTM 50 & 98 & 0.12 & 98 & 0.001\\
-RMBPTM 100 & 98 & 0.12 & 98 & 0.002\\
-RMBPTM 1,000 & 78 & 3.10 & 78 & 0.002\\
-RMBPTM 10,000 & 70 & 168.87 & 70 & 0.006 \\
+RMBPTM 20 & 100 & 0.10 & 100 & 0.002 \\
+RMBPTM 50 & 98 & 0.07 & 98 & 0.002\\
+RMBPTM 100 & 98 & 0.11 & 98 & 0.002\\
+RMBPTM 1,000 & 78 & 9.59 & 78 & 0.013\\
+RMBPTM 2,000 & 70 & 3.24 & 70 & 0.027\\
+RMBPTM 5,000 & 70 & 15.28 & 70 & 0.079 \\
+RMBPTM 10,000 & 70 & 58.22 & 70 & 0.185 \\
 \cline {1-5} \\

### 2023-08-14 manuscriptBlinded.tex
paper before submiting

--- 2023-08-14 manuscript.tex
@@
 
-%\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}
-
-\author{Tatiana Balbi Fraga\corref{cor1}\fnref{label1}}
-\ead{tatiana.balbi@ufpe.br}
-\cortext[cor1]{corresponding author}
-
-\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
-\ead{italo_ruan_@hotmail.com}
-
-\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
-\ead{regilda.smenezes@ufpe.br}
-
 %\affiliation[label1]{
@@
 %             country={Brasil} }
-
-\affiliation[label1]{
-		   organization={Agreste Academic Center - Federal University of Pernambuco},%Department and Organization
-           addressline={Avenida Marielle Franco, Nova Caruaru}, 
-           city={Caruaru},
-           postcode={55014-900}, 
-           state={PE},
-           country={Brazil}}
 
@@
 \label{sec:intro}
-
-Starting a working day... 
-Tasks finish tests using LINGO on optimization mode.
-Submit paper again to journal.
 
@@
 \begin{algorithm}
-\caption{Solving MBPTMP | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
+\caption{Solving MBPTM problem | Part 01 - find an optimal $T$ to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}).}\label{alg:part01}
 \begin{algorithmic}
@@
 \begin{algorithm}
-\caption{Solving MBPTMP | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions in (\ref{eq:resO}) and (\ref{eq:resI}).}\label{alg:part02}
+\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions in (\ref{eq:resO}) and (\ref{eq:resI}).}\label{alg:part02}
 \begin{algorithmic}
@@
 \begin{algorithm}
-\caption{Solving MBPTMP | Part 03: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part03}
+\caption{Solving MBPTM problem | Part 03: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part03}
 \begin{algorithmic}
@@
 
-\emph{Solution for the example presented before - determining the values of $D_i$, $O_i$ and $I_i$, $\forall i$.}
-
-$T = 55 \textrm{min}$
-
-$E_A = 55 \textrm{min}* 60 \textrm{ g}/\textrm{min}  = 3,300 \textrm{ g}$
-
-$E_B = 55 \textrm{min}* 40 \textrm{ g}/\textrm{min}  = 2,200 \textrm{ g}$
-
-$D_A = \min \{1,000 \textrm{ g}, \textrm{ } 3,300 \textrm{ g}\} = 1,000 \textrm{ g} $
-
-$D_B = \min \{500 \textrm{ g}, \textrm{ } 2,200 \textrm{ g}\} = 500 \textrm{ g} $
-
-$E_A = 3,300 \textrm{ g} - 1,000 \textrm{ g} = 2,300 \textrm{ g}$
-
-$E_B = 2,200 \textrm{ g} - 500 \textrm{ g} = 1,700 \textrm{ g}$
-
-$O_A = \min \{600 \textrm{ g}, \textrm{ }  2,000 \textrm{ g}\} = 600 \textrm{ g}$
-
-$O_B = \min \{600 \textrm{ g}, \textrm{ }  1,700 \textrm{ g}\} = 600 \textrm{ g}$
-
-$E_A = 2,300 \textrm{ g} - 600 \textrm{ g} = 1,700 \textrm{ g}$
-
-$E_B = 1,700 \textrm{ g} - 600 \textrm{ g} = 1,100 \textrm{ g}$
-
-$\textrm{UO}_A = 600 \textrm{ g} - 600 \textrm{ g} = 0 \textrm{ g}$
-
-$\textrm{UO}_B = 600 \textrm{ g} - 600 \textrm{ g} = 0 \textrm{ g}$
-
-$I_A = 1,700 \textrm{ g}$
-
-$I_B = 1,100 \textrm{ g}$
-
-$\textrm{UI}_A = 3,000 \textrm{ g} - 1,700 \textrm{ g} = 1,300 \textrm{ g}$
-
-$\textrm{UI}_B = 2,000 \textrm{ g} - 1,100 \textrm{ g} = 900 \textrm{ g}$
-
-$SO = 1,000 \textrm{ g} - 1,200 \textrm{ g} = - 200 \textrm{ g}$
-
-$SI = 3,000 \textrm{ g} - 2,800 \textrm{ g} = 200 \textrm{ g}$
-
-\emph{Redistribution}
-
-$O_A = 600 \textrm{ g} - \min \{600 \textrm{ g}, \textrm{ }  1,300 \textrm{ g}, \textrm{ }  200 \textrm{ g}\} = 400 \textrm{ g}$
-
-$I_A = 1,700 \textrm{ g} + \min \{600 \textrm{ g}, \textrm{ }  1,300 \textrm{ g}, \textrm{ }  200 \textrm{ g}\} = 1,900 \textrm{ g}$
-
-$SO = 200 \textrm{ g} + \min \{600 \textrm{ g}, \textrm{ }  1,300 \textrm{ g}, \textrm{ }  200 \textrm{ g}\} = 0 \textrm{ g}$
-
-\emph{Solution}
-
-$T = 55 \textrm{min}; \quad D_A = 1,000 \textrm{ g}; \quad D_B = 500 \textrm{ g}; \quad O_A = 400 \textrm{ g}; \quad O_B = 600 \textrm{ g}; \quad I_A = 1,900 \textrm{ g}; \quad \textrm{and } I_B = 1,100 \textrm{ g}$.
-
 \section{Tests and results}
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230809, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MPBPTM.lng both available at https://github.com/tbfraga/COPSolver.
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/Blinded.
 The tests were performed on a notebook with an Intel i7 processor.
@@
 To build the results presented in this work, we used source=0.
-The benchmarks used for the tests performed can be consulted at github.com/tbfraga/COPSolver.
+The benchmarks used for the tests performed can be consulted at github.com/Blinded.
 
@@
 \cline {1-5} \\
-MBPTM 2 & 55 & 0.04 & 55 & 0.001 \\
-MBPTM 3 & 48 & 0.06 & 48 & 0.001 \\
-MBPTM 10 & 30 & 0.09 & 30 & 0.001 \\
-RMBPTM 20 & 100 & 0.10 & 100 & 0.002 \\
-RMBPTM 50 & 98 & 0.07 & 98 & 0.002\\
-RMBPTM 100 & 98 & 0.11 & 98 & 0.002\\
-RMBPTM 1,000 & 78 & 9.59 & 78 & 0.013\\
-RMBPTM 2,000 & 70 & 3.24 & 70 & 0.027\\
-RMBPTM 5,000 & 70 & 15.28 & 70 & 0.079 \\
-RMBPTM 10,000 & 70 & 58.22 & 70 & 0.185 \\
+MBPTM 2 & 55 & 0.03 & 55 & $<$ 0.01 \\
+MBPTM 3 & 48 & 0.03 & 48 & $<$ 0.01 \\
+MBPTM 10 & 30 & 0.05 & 30 & $<$ 0.01 \\
+RMBPTM 20 & 100 & 0.06 & 100 & $<$ 0.01 \\
+RMBPTM 50 & 98 & 0.08 & 98 & $<$ 0.01 \\
+RMBPTM 100 & 98 & 0.11 & 98 & $<$ 0.01 \\
+RMBPTM 1,000 & 78 & 1.20 & 78 & $<$ 0.01 \\
+RMBPTM 2,000 & 70 & 3.25 & 70 & $<$ 0.01 \\
+RMBPTM 5,000 & 70 & 15.12 & 70 & $<$ 0.02 \\
+RMBPTM 10,000 & 70 & 55.19 & 70 & $<$ 0.04 \\
 \cline {1-5} \\
@@
 Tables (\ref{tab:compResultsMBPTMP2}) and (\ref{tab:compResultsMBPTMP3}) shows the production distribution for MBPTM 3 and 10 found by both COPSolver and LINGO solver.
-Files containing all results can be found at github.com/tbfraga/COPSolver.
+Files containing all results can be found at github.com/Blinded.
 
@@
 
-T.B.
-Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing.
-Í.R.B.
-Aquino: Data curation.
-R.C.S.
-Menêzes: Data curation.
+Blinded
 

### 2023-08-18 multi-period/manuscript.tex
updating papers
multi-period

@@
 \documentclass[authoryear,preprint,12pt]{elsarticle}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 
+$\textrm{UI}_i$ is the factory free inventory for product $p$ on day 0;
+
 $\textrm{p}_i$ is the production rate of product $i$;
 
-$\textrm{Z}$ is the timeout for batch processing; \\
+$\textrm{Z}$ is the timeout for batch processing;
 
@@
 
-being $\textrm{UI}_{i0}$ the maximum quantity allowed for $P_i$;
-
 $I_{d}$ is the free factory storage of all products on the end of the day $d$;
 
-being $\textrm{I}_{0}$ the initial free inventory for all products on factory on the start of the (\emph{first}) planning day ($d=1$); \\
+being $\textrm{I}$ the initial free inventory for all products on factory on the start of the (\emph{first}) planning day ($d=1$); \\
 
@@
 \label{eq:mmeq03}
-P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i0} - \textrm{PO}_{i1}
+P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i} - \textrm{PO}_{i1}
 \end{equation}
@@
 
-Uma solução ótima para este problema pode ser construída através de duas etapas, conforme explicado a seguir: \\
+Uma solução ótima para este problema pode ser construída através de seis etapas, conforme algoritmos apresentados a seguir: \\
 
-\emph{etapa 1: distribuição da produção previamente planejada} \\
+\begin{algorithm}
+\caption{Solving MMBPTM problem | Part 01 - distribution planned production ignoring restrictions defined for the set.}\label{alg:part01}
+\begin{algorithmic}
+	\Require $\textrm{UD}_{id}, \textrm{PO}_{id}, \textrm{UO}_i, \textrm{UI}_i, \forall i; \textrm{O}, \textrm{I}$.
 
-passo 1: Desconsidere a produção a ser planejada:
+	\State $I_{1} \gets \textrm{I} - \sum\{\textrm{PO}_{i1}\}$
+	\State $O \gets \textrm{O}$
 
-\begin{equation}
-\label{eq:sm01}
-P_i = 0, \forall i
-\end{equation}
+	\For{all $i$}
+		\State $D_{i1} \gets \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\}$
+		\State $UI_{i1} \gets \textrm{UI}_i - \textrm{PO}_{i1} + D_{i1}$
+		\State $I_{1} \gets I_{1} + D_{i1}$
 
-passo 2:
+		\If{$UI_{i1} < 0$}
+			\State $O_{i1} \gets - UI_{i1}$
+			\State $UO_i \gets \textrm{UO}_i - O_{i1}$
+			\State $O \gets O - O_{i1}$
+			\State $I_{1} \gets I_{1} + O_{i1}$
+			\State $UI_{i1} \gets 0$
+			\If{$UO_i < 0 \textbf{ or } O < 0$}
+			\State \textbf{Return:} planning is not feasible
+			\EndIf
+		\EndIf
+	\EndFor
 
-Calcule $D_{i1}$ usando as equações em (\ref{eq:sm02}):
+	\For{all $d>1$}
 
-\begin{equation}
-\label{eq:sm02}
-D_{i1} = \min \{\textrm{UD}_{i1}, \textrm{PO}_{i1}\} \quad \forall i
-\end{equation}
+		\State $I_{d} \gets  I_{d-1} - \sum\{\textrm{PO}_{id}\}$
 
-Calcule o valor da produção não ainda não alocada, $\textrm{S}_{id}, \forall i$, pelas equações em (\ref{eq:sm03}):
+		\For{all $i$}
+			\State $UD_{id} \gets \sum_{k=1}^{d}\{\textrm{UD}_{ik}\} - \sum_{k=1}^{d-1}\{D_{ik}\}$
+			\State $A_{id} \gets \min\{\sum_{k=1}^{d-1}\{\textrm{PO}_{ik} - D_{ik} - O_{ik}\}\}  + 						\textrm{PO}_{id}$ 
+			\State $D_{id} \gets  \min\{UD_{id}, A_{id}\}$
+			\State $UI_{id} \gets UI_{i(d-1)} - \textrm{PO}_{id} + D_{id}$
 
-\begin{equation}
-\label{eq:sm03}
-\textrm{S}_{i1} = \textrm{PO}_{i1} - D_{i1}, \quad \forall i
-\end{equation}
+			\State $I_{d} \gets I_{d} + D_{id}$
 
-Calcule os valores $D_{id}^+$, $\textrm{S}_{id}^+$, $D_{id}^-$ e $\textrm{S}_{id}^-, \forall i$, usando as equações de (\ref{eq:sm04}) à (\ref{eq:sm08}).
+			\If{$UI_{id} < 0$}
+				\State $O_{i1} = - UI_{i1}$
+				\State $UO_i = UO_i - O_{id}$
+				\State $O \gets O - O_{id}$
+				\State $I_{d} \gets I_{d} + O_{id}$
+				\State $UI_{id} = 0$
+				\If{$UO_i < 0 \textbf{ or } O < 0$}
+					\State \textbf{Return:} planning is not feasible
+				\EndIf
+			\EndIf
+		\EndFor
+	\EndFor
 
-\begin{equation}
-\label{eq:sm04}
-D_{i1}^+ = D_{i1}^- = D_{i1}
-\end{equation}
+	\State \textbf{Return:} $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.
+\end{algorithmic}
+\end{algorithm}
 
-\begin{equation}
-\label{eq:sm05}
-D_{id}^+ =  \min\{(\sum_{k=1}^{d}{\textrm{UD}_{ik}} - \sum_{k=1}^{d-1}{D_{ik}}), (\sum_{k=1}^{d-1}{(\textrm{PO}_{ik} - D_{ik}^+) + \textrm{PO}_{id}})\}  \quad \forall i, \forall (d>1)
-\end{equation}
+\begin{algorithm}
+\caption{Solving MMBPTM problem | Part 02 - adjustment for atteining feasiability.}\label{alg:part02}
+\begin{algorithmic}
+	\Require $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.
 
-\begin{equation}
-\label{eq:sm06}
-\textrm{S}_{id}^+ = \textrm{PO}_{id} - D_{id}^+, \quad \forall i, \forall (d>1)
-\end{equation}
+	\For{all $d$}
+		\If{$I_{d} < 0$}
+			\For{all $i$}
+				\If{$UO_i \geq |I_{d}|$}
+					\State $O_{id} \gets O_{id} - I_{d}$
+					\State $UO_i \gets UO_i + I_{d}$
+					\State $O \gets O + I_{d}$
+					\For{all $k \geq d$}
+						\State $UI_{ik} \gets UI_{ik} - I_{d}$
+						\State $I_{k} \gets I_{k} - I_{d}$
+					\EndFor
+					\State break;
+				\Else 
+					\State $O_{id} \gets O_{id} + UO_i$
+					\State $UO_i \gets 0$
+					\State $O \gets O - UO_i$
+					\For{all $k \geq d$}
+						\State $UI_{ik} \gets UI_{ik} + UO_i$
+						\State $I_{k} \gets I_{k} + UO_i$
+					\EndFor
+				\EndIf
+			\EndFor
+		\EndIf
+	\EndFor
 
-\begin{equation}
-\label{eq:sm07}
-D_{id}^- =  \min\{(\sum_{k=2}^{d}{\textrm{UD}_{ik}} - \sum_{k=2}^{d-1}{D_{ik}}), (\sum_{k=1}^{d-1}{(\textrm{PO}_{ik} - D_{ik}^-) + \textrm{PO}_{id}})\}  \quad \forall i, \forall (d>1)
-\end{equation}
+	\State \textbf{Return:} $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.
+\end{algorithmic}
+\end{algorithm}
 
-\begin{equation}
-\label{eq:sm08}
-\textrm{S}_{id}^- = \textrm{PO}_{id} - D_{id}^-, \quad \forall i, \forall (d>1)
-\end{equation}
+\begin{algorithm}
+\caption{Solving MMBPTM problem | Part 03 - generating a MBPTM problem.}\label{alg:part03}
+\begin{algorithmic}
+	\Require $O_{id}, UI_{id}, \forall (i, d); I_d, \forall d; UO_i, \forall i; O$.
 
-Queremos encontrar $D_{id}$, $ D_{id}^- \leq D_{id} \leq D_{id}^+, \forall i,(d>1) $, tal que as restrições em (\ref{eq:sm09}) sejam respeitadas:
+	\For{all $i$}
+		\State $\textrm{UD}_{i} = UD_{i1}$
+		\State $\textrm{UO}_i = UO_i$
+		\State $\textrm{UI}_i = \min_d\{UI_{id}\}$
+	\EndFor
 
-\begin{equation}
-\label{eq:sm09}
-D_{id} = \min {x \in \{D_{id}^-, D_{id}^+ \quad | \quad UI_{id} \geq 0\}} \quad \forall i, \forall (d>1)
-\end{equation}
+	\State $\textrm{O} = O$
+	\State $\textrm{I} = \min_d\{I_{d}\}$
 
-Contudo, para solução do problema, iremos adotar:
+	\State \textbf{Return:} $\textrm{UD}_{i}, \textrm{UO}_i, \textrm{UI}_i, \forall i; \textrm{O}, \textrm{I}$.
+\end{algorithmic}
+\end{algorithm}
 
-\begin{equation}
-\label{eq:sm10}
-D_{id} = D_{id}^- \quad \forall i, \forall (d>1)
-\end{equation}
+\begin{algorithm}
+\caption{Solving MMBPTM problem | Part 04 - find an optimal $T$ to the MBPTM problem.}\label{alg:part04}
+\begin{algorithmic}
+	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}$
+	\State $T^* \gets \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor$
+	\State $T \gets \min \{T^* , \textrm{Z}\}$
+\State \textbf{Return:} $T$.
+\end{algorithmic}
+\end{algorithm}
 
-\begin{equation}
-\label{eq:sm10}
-\textrm{S}_{id} = \textrm{S}_{id}^- \quad \forall i, \forall (d>1)
-\end{equation}
+\begin{algorithm}
+\caption{Solving MMBPTM problem | Part 05 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions defined for the set.}\label{alg:part05}
+\begin{algorithmic}
+	\Require $\textrm{UD}_i, \textrm{UO}_i, \textrm{UI}_i, \textrm{p}_i, \forall i, \textrm{O}, \textrm{I}, \textrm{Z}, T$.
+	\For{all i}
+		\State $P_i \gets T * \textrm{p}_i$
+		\State $D_i \gets \min \{\textrm{UD}_i, E_i\}$
+		\State $E_i \gets P_i - D_i$
+		\State $O_i \gets \min \{\textrm{UO}_i, E_i\}$
+		\State $E_i = E_i - O_i$
+		\State $\textrm{UO}_i = \textrm{UO}_i - O_i$
+		\State $I_i = E_i$
+		\State $\textrm{UI}_i = \textrm{UI}_i - I_i$
+	\EndFor
+	\State $SO = \textrm{O} - \sum_i{O_i}$
+	\State $SI = \textrm{I} - \sum_i{I_i}$
+	\State \textbf{Return:} $D_i, O_i, I_i, P_i, E_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
+\end{algorithmic}
+\end{algorithm}
 
-passo 3: Calcule os valores $O_{id}, \forall i, d$, usando as equações em (\ref{eq:sm11}):
+\begin{algorithm}
+\caption{Solving MMBPTM problem | Part 06: redistribute production to comply with limitation restrictions for the batch products set.}\label{alg:part06}
+\begin{algorithmic}
+\Require $O_i, I_i, \textrm{UO}_i, \textrm{UI}_i, \forall i, SO, SI$.
+\If{$SO < 0$}
+\For{all $i$}
+	\State $O_i \gets O_i - \min\{ O_i, UI_i, |SO|\}$
+	\State $I_i \gets I_i + \min\{ O_i, UI_i, |SO|\}$
+	\State $SO \gets SO + \min\{ O_i, UI_i, |SO|\}$
+	\If{$SO = 0$}
+		break looping for;
+	\EndIf
+\EndFor
+\EndIf
 
-\begin{equation}
-\label{eq:sm11}
-O_{id} = \min \{\textrm{S}_{id}, (\textrm{UO}_i - \sum_{k=1}^{d-1}{O_{ik}}) , (\textrm{O}- \sum_{j=1}^{i-1}\sum_{k=1}^{d-1}{O_{jk}}) \} \quad \forall i, d
-\end{equation}
-
-passo 4:
-
-calcule os valores para $UI_{id}, \forall i, d$, usando as equações em (\ref{eq:mmeq03}) e (\ref{eq:mmeq04})).
-
-calcule os valores para $I_{i}, \forall i$, usando as equações em (5) e (6). \\
-
-\emph{Step 2: MPBPTM problem construction} \\
-
-So, based on calculated values, we built the MPBPTM problem using the equations:
-
-\begin{equation}
-\textrm{UD}_{i} = \textrm{UD}_{i1} - D_{i1} \quad \forall i
-\end{equation}
-
-\begin{equation}
-\textrm{I} = \min_{d} \{I_{d}\}
-\end{equation}
-
-\begin{equation}
-\textrm{UI}_{i} = \min_{d} \{UI_{id}\}, \quad \forall{i}
-\end{equation}
-
-\begin{equation}
-\textrm{O} = \textrm{O} - \sum_{i}{\sum_{d}{O_{id}}}
-\end{equation}
-
-\begin{equation}
-\textrm{UO}_{i} = \textrm{UO}_{i} - \sum_{d}{O_{id}}, \quad \forall i
-\end{equation} \\
-
-Being $\textrm{p}_{i}$ and $\textrm{Z}$ defined according to the MPMPBPTM problem presented. \\
-
-Obs: Note that some values of $UI_{id}$ and  $I_{d}$ can be negative.
-This means that, in prior planning, some demand of the first day will be met by some previous planned production performed in a future period and that cannot be modified, i.e.
-$D_{id} > D_{id}^-$ for at least one ordained pair $(i,d)$.
-In this case, considering that prior planning was a viable planning, the negative values of the $UI_{id}$ and $I_{d}$ will be offset by the positive surplus values of $\textrm{UD}_{i}$, so this will not result in change in the optimal solution of the problem through the method used in the next step.
-\\
-
-The possible negative maximum values for variables are defined by the following equations. If this equations are not met, it means that initial planning was not a viable planning.
-
-\begin{equation}
-\max_d\{UI_{id}\} \geq \textrm{UD}_{i1} - D_{i1}, \quad \forall i
-\end{equation}
-
-\begin{equation}
-\max_d\{I_{d}\} \geq \sum_{i}\{ \textrm{UD}_{i1} - D_{i1} \}
-\end{equation}
-
-\emph{Step 3: MPBPTM solution by Fraga's analytical method} \\
-
-Once the MPBPTM problem is built, it can be solved by the analytical method proposed by Fraga (Fraga et al., 2023). This method can be resumed into two steps, as follows: \\
-
-step 1: find $T^*$, where:
-\begin{equation}
-T^* = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + \textrm{UD}_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i \textrm{UD}_i) / \sum_i {\textrm{p}_i}\}}\rfloor
-\end{equation}
-
-step 2: calculate $T$, where:
-
-\begin{equation}
-T = \min \{T^* , \textrm{Z}\}
-\end{equation} \\
-
-\emph{Solution for the example presented before} \\
-
-Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have: \\
-
-Como planejamento prévio de produção, temos:
-
-$\textrm{P}_{11} = 1000$,
-$\textrm{P}_{12} = 0$,
-$\textrm{P}_{21} = 0$,
-$\textrm{P}_{22} = 1500$. \\
-
-Como demanda, temos:
-
-$\textrm{UD}_{11} = 1000$,
-$\textrm{UD}_{12} = 500$,
-$\textrm{UD}_{21} = 500$,
-$\textrm{UD}_{22} = 300$. \\
-
-Distribuindo a produção para atender à demanda de acordo com as restrições em (9) e (10), temos: \\
-
-$D_{11} = 1000$,
-$D_{12} = 0$,
-$D_{21} = 0$,
-$D_{22} = 300$. \\
-
-Não há nenhuma sobra relativa a produção de A. E há uma sobra de produção de 1200 unidades de B no segundo dia. \\
-
-Como estoque livre nos outlets, temos:
-
-$\textrm{UO}_{1} = 600$;
-$\textrm{UO}_{2} = 600$;
-$\textrm{O} = 1000$; \\
-
-Assim, distribuindo a sobra da produção para os outlets de acordo com as restrições em (7) e (8), temos:
-
-$O_{11} = 0$,
-$O_{12} = 0$,
-$O_{21} = 0$,
-$O_{22} = 600$. \\
-
-Com relação ao estoque livre em fábrica, temos:
-
-$\textrm{UI}_{10} = 3000$,
-$\textrm{UI}_{20} = 2000$,
-$\textrm{I}_{0} = 3000$. \\
-
-Portanto, calculando os valores disponíveis para produção de acordo com as equações em (3), (4) e (5), temos:
-
-$UI_{11} = 3000 - 1000 + 1000 + 0 =  3000$,
-$UI_{12} = 3000 - 0 + 0 + 0 =  3000$,
-$UI_{21} = 2000 - 0 + 0 + 0 =  2000$,
-$UI_{22} = 2000 - 1500 + 300 + 600 =  1400$. \\
-
-$I_{1} = 3000 - 1000 + 1000 + 0 = 3000$,
-$I_{2} = 3000 - 1500 + 300 + 600 = 2400$. \\
-
-Portanto temos agora as informações referentes aos limites estocagem em fábrica diário para cada produto assim como o limite de estocagem em fábrica diário para todos os produtos. \\
-
-Definindo o problema MPBPTM, temos: \\
-
-$\textrm{UD}_{1} = 1000 - 1000 = 0$,
-$\textrm{UD}_{2} = 0$ . \\
-
-$\textrm{I} = \min_{d} \{3000, 2400\} = 2400$. \\
-
-$ \textrm{UI}_{1} = \min_{d} \{3000, 3000\} = 3000 $,
-$ \textrm{UI}_{2} = \min_{d} \{2000, 1400\} = 1400 $. \\
-
-$\textrm{O} = 1000 - 600 = 400.$ \\
-
-$\textrm{UO}_{1} = 600 - 0 = 600$, 
-$\textrm{UO}_{2} = 600 - 600 = 0$. \\
-
-$\textrm{p}_{1} = 60$,
-$\textrm{p}_{2} = 40$.  \\
-
-$\textrm{Z} = 100$.  \\
-
-Então, aplicando o método de partição do tempo proposto pro Fraga, temos: \\
-
-$T' = 0 \textrm{ min}$ \\
-
-Then:\\
-
-$S_A = 0 \textrm{ g}$ \\
-
-$S_B = 0 \textrm{ g}$ \\
-
-And so we have: \\
-
-$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 0 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 60 \textrm{ min}$ \quad for A \\
-
-$T'' \leq \lfloor{(1400 \textrm{ g} + 0 \textrm{ g} + 0 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 35 \textrm{ min}$ \quad for B \\
-
-$T'' \leq \lfloor{(400 \textrm{ g} + 2400 \textrm{ g} + 0 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$ \\
-
-$T'' \leq 28 \textrm{ min}$ \quad for A and B \\
-
-So that: \\
-
-$T'' = 28 \textrm{ min}$ \\
-
-So we have: \\
-
-$T = 28 \textrm{ min}$ \\
-
-As $T<\textrm{Z}$, then $T = 28 \textrm{ min}$ will certainly be the optimal solution. \\
-
-In this case we will have: \\
-
-$P_A = 1,680  \textrm{ g}$ e $P_B=1,120 \textrm{ g}$ \\
-
-$D_A = 0 \textrm{ g}$ e $D_B = 0 \textrm{ g}$ \\
-
-$E_A = 1,680 \textrm{ g}$ e $E_B = 1,120 \textrm{ g}$ \\
+\If{$SI < 0$}
+\For{all $i$}
+	\State $I_i \gets I_i - \min\{ I_i, UO_i, |SI|\}$
+	\State $O_i \gets O_i + \min\{ I_i, UO_i, |SI|\}$
+	\State $SI \gets SI + \min\{ I_i, UO_i, |SI|\}$
+	\If{$SI = 0$}
+		break looping for;
+	\EndIf
+\EndFor
+\EndIf
+\State \textbf{Return:} $O_i, I_i, \forall i$.
+\end{algorithmic}
+\end{algorithm}
 

### 2023-08-22 manuscript.tex
updating paper
explaining better exact method

@@
 
-Starting a working day... 
-Tasks finish tests using LINGO on optimization mode.
-Submit paper again to journal.
-
 The scientific literature presents several papers that address multi-product batch problems.
@@
 
+O método proposto neste artigo para solução do MBPTM problem é composto por duas partes distintas, que são: a) cálculo do tempo máximo de processamento do lote multi-produtos; e b) cálculo e distribuição da produção entre a demanda, os outlets e o estoque em fábrica.
+A seguir, explicamos cada uma destas partes detalhadamente.
+
+\noindent \emph{cálculo do tempo máximo de processamento do lote multi-produtos:}
+
+It is possible to split the batch processing time into two time slots:
+
+\begin{equation}
+T = T' + T''
+\end{equation}
+
+\noindent where $T'$ é o tempo máximo de processamento cuja produção será utilizada exclusivamente para atendimento da demanda.
+
+Neste caso, sendo $D_{i}^{'}$ a quantidade produzida do produto $i$ após $T'$ unidades de tempo de processamento do lote, temos que:
+
+\begin{equation}
+\label{eq:s02}
+D_{i}^{'} - \textrm{p}_i * T'  = 0 \quad \forall i
+\end{equation}
+
+\begin{equation}
+\label{eq:s03}
+D_{i}^{'} \in Z \quad \forall i
+\end{equation}
+
+\noindent e, como $D_{i}^{'} \leq D_i$, $\forall i$, temos que:
+
+\begin{equation}
+\label{eq:s04}
+D_{i}^{'} \leq \textrm{UD}_i\quad \forall i
+\end{equation}
+
+Das equações em (\ref{eq:s02}), (\ref{eq:s03}) e (\ref{eq:s04}), temos:
+
+\begin{equation}
+\label{eq:s05}
+T' \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
+\end{equation}
+
+E, como desejamos máximo valor para $T'$, de (\ref{eq:s05}), temos:
+
+\begin{equation}
+\label{eq:s06}
+T' = \min_i\{\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor\}
+\end{equation}
+
+Observer que poderá haver uma sobra correspondente à demanda não atendida pela produção ocorrida na primeira parte do tempo de processamento do lote, $T'$.
+Esta sobra, $S_i$, será definida de acordo com as equações em (\ref{eq:s07}):
+
+\begin{equation}
+\label{eq:s07}
+S_i = \textrm{UD}_i - D_{i}^{'} \quad \forall i
+\end{equation}
+
+É possível também considerar que os outlets são uma extensão do estoque da fábrica.
+Portanto it is possible to consider the factory stock of product $i$ and the outlets stock $i$ as single stock for the product $i$, de forma que:
+
+\begin{equation}
+\label{eq:s08}
+E_i = O_i + I_i
+\end{equation}
+
+\begin{equation}
+\label{eq:s09}
+E_i \leq \textrm{UO}_i + \textrm{UI}_i
+\end{equation}
+
+\begin{equation}
+\label{eq:s10}
+\sum_i {E_i} \leq \textrm{O} + \textrm{I}
+\end{equation}
+
+\begin{equation}
+\label{eq:s11}
+E_i \in Z \quad \forall i
+\end{equation}
+
+\noindent where $E_i$ is the sum of factory stock and outlets stock of the product $i$.
+
+Como o tempo $T'$ foi utilizado apenas para produção que irá atender à demanda, $T''$ será o restante do tempo de processamento, ou seja, o tempo máximo de processamento utilizado para produção que irá atender à sobra da demanda, será enviada para os outlets e estocada em fábrica.
+Assim temos que:
+
+\begin{equation}
+\label{eq:s12}
+E_i + S_i - \textrm{p}_i * T''  = 0 \quad \forall i
+\end{equation}
+
+Portanto, das restrições em (\ref{eq:s09}) e equações em (\ref{eq:s12}), temos:
+
+\begin{equation}
+\label{eq:s13}
+T''  \leq (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i \quad \forall i
+\end{equation}
+
+\noindent e, das restrições em (\ref{eq:s10}) e equações em (\ref{eq:s12}), temos:
+
+\begin{equation}
+\label{eq:s14}
+ T'' \leq (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i
+\end{equation}
+
+Finalmente, como $T''$ é um valor inteiro e queremos maximizar esse valor, então:
+
+\begin{equation}
+\label{eq:s15}
+ T'' = \lfloor\min\{ \min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
+\end{equation}
+
+\noindent Assim, $T$ pode ser calculado conforme equação em (\ref{eq:s17}):
+
+\begin{equation}
+\label{eq:s17}
+ T = \lfloor \min_i\{{\textrm{UD}_i / \textrm{p}_i}\} + \min\{ \min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
+\end{equation}
+
 To solve the MBPTM problem we will start considering that, despite equations in (10) and (11) define a priority for production distribution, $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory.
@@
 
-After relaxation of the problem, it is possible to consider the factory stock and the outlets stock as single stock, so we have:
-
-\begin{equation}
-E_i = O_i + I_i
-\end{equation}
-
-where $E_i$ is the sum of the quantity stored at the factory and the quantity sent to the outlets of the product $i$.
+After relaxation of the problem,
 
@@
 
-\emph{Solution for the example presented before}
-
-Applying the method for solving the example presented in section \ref{sec:MBPTMP}, we have:
-
-$T' \leq \lfloor{1000 \textrm{ g} / (60 \textrm{ g}/\textrm{min})}\rfloor$
-
-$T' \leq 16 \textrm{ min}$ \quad for A
-
-$T' \leq \lfloor{500 \textrm{ g} / (40 \textrm{ g}/\textrm{min})}\rfloor$
-
-$T' \leq 12 \textrm{ min}$ \quad for B
-
-so:
-
-$T' = 12 \textrm{ min}$
-
-Then:
-
-$S_A = 1000 \textrm{ g} - 12 \textrm{ min} * 60 \textrm{ g}/\textrm{min} = 280 \textrm{ g}$
-
-$S_B = 500 \textrm{ g} - 12 \textrm{ min} * 40 \textrm{ g}/\textrm{min} = 20 \textrm{ g}$
-
-And so we have:
-
-$T'' \leq \lfloor{(3000 \textrm{ g} + 600 \textrm{ g} + 280 \textrm{ g}) / (60 \textrm{ g}/\textrm{min})}\rfloor$
-
-$T'' \leq 64 \textrm{ min}$ \quad for A
-
-$T'' \leq \lfloor{(2000 \textrm{ g} + 600 \textrm{ g} + 20 \textrm{ g}) / (40 \textrm{ g}/\textrm{min})}\rfloor$
-
-$T'' \leq 65 \textrm{ min}$ \quad for B
-
-$T'' \leq \lfloor{(1000 \textrm{ g} + 3000 \textrm{ g} + 300 \textrm{ g}) / (100 \textrm{ g}/\textrm{min})}\rfloor$
-
-$T'' \leq 43 \textrm{ min}$ \quad for A and B
-
-So that:
-
-$T'' = 43 \textrm{ min}$
-
-So we have:
-
-$T = 55 \textrm{ min}$
-
-As $T<\textrm{Z}$, then $T = 55 \textrm{ min}$ will certainly be the optimal solution.
-
-In this case we will have:
-
-$P_A = 3300 \textrm{ g}$ e $P_B=2200 \textrm{ g}$
-
-$D_A = 1000 \textrm{ g}$ e $D_B = 500 \textrm{ g}$
-
-$E_A = 2300 \textrm{ g}$ e $E_B = 1700 \textrm{ g}$
-
 After determining a solution, the values of $D_i$, $O_i$ and $I_i$, $\forall i$, can be found by taking a solution from the undetermined system of inequalities:
@@
 
-To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230809, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MPBPTM.lng both available at https://github.com/tbfraga/COPSolver.
+To test the developed model and analytical solution method, we created a solver in C++ named COPSolver (V01\_20230814, lib multiproduct-batch-processing-time-maximization-problem) and a solver in LINGO named MBPTM.lng both available at https://github.com/tbfraga/COPSolver.
 The tests were performed on a notebook with an Intel i7 processor.

### 2023-08-22 manuscript.tex
updating paper

@@
 \label{eq:s15}
- T'' = \lfloor\min\{ \min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
+ T'' = \lfloor\min\{\min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
 \end{equation}
@@
 \label{eq:s17}
- T = \lfloor \min_i\{{\textrm{UD}_i / \textrm{p}_i}\} + \min\{ \min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor
+ T = \min\{Z, \lfloor \min_i\{{\textrm{UD}_i / \textrm{p}_i}\} + \min\{ \min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor\}
 \end{equation}
 
-To solve the MBPTM problem we will start considering that, despite equations in (10) and (11) define a priority for production distribution, $T$ is not affected by the way production is distributed betwing demand, outlets and factory inventory.
-So we can find $T$, by ignoring this equations and, after finding $T$ for the relaxed model, solving the production distribution problem based on the defined priorities.
-
-After relaxation of the problem,
-
-So that:
-
-\begin{equation}
-E_i \leq \textrm{UO}_i + \textrm{UI}_i
-\end{equation}
-
-and
-
-\begin{equation}
-\sum_i {E_i} \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-It is also possible to split the batch processing time into two time slots:
-
-\begin{equation}
-T = T' + T''
-\end{equation}
-
-and consider that $T'$ is the maximum processing time used only for production that will meet the demand. Thus, we can find $T'$, solving the reduced problem:
-
-\begin{equation}
-max \quad T'
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-D_i - \textrm{p}_i * T'  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i, T' \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-This reduced problem can be rewritten in the form:
-
-\begin{equation}
-max \quad T'
-\end{equation}
-
-$s.t.$ \\
-
-\begin{equation}
-T'  \leq \lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor \quad \forall i
-\end{equation}
-
-So we have that $T'$ will be the smallest of the ratios $\lfloor{\textrm{UD}_i / \textrm{p}_i}\rfloor$ of all products. \\
-
-Once we find the value of $T'$, we can calculate the value of unmet demand for each product after $T'$, $S_i$, through the equations in (\ref{eq:unmet1}).
-
-\begin{equation}
-\label{eq:unmet1}
-S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
-\end{equation}
-
-Now we consider that the time interval $T''$ will be used for the production of the quantities that will be stored (in the factory and in the outlets), as well as of the demand not met by the production in the first time interval, $S_i$.
-
-In this case, we can find $T''$ by solving the second reduced problem:
-
-\begin{equation}
-max \quad T''
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-E_i - \textrm{p}_i * T''  = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-E_i - S_i \leq \textrm{UO}_i + \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\sum_i ({E_i - S_i}) \leq \textrm{O} + \textrm{I}
-\end{equation}
-
-\begin{equation}
-E_i, T'' \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-Again, using a little algebra, we can rewrite this reduced problem in the form:
-
-\begin{equation}
-max \quad T''
-\end{equation}
-
-$s.t.$
-
-\begin{equation}
-T'' \leq \lfloor{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i}\rfloor  \quad \forall i
-\end{equation}
-
-\begin{equation}
-T'' \leq \lfloor{(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}}\rfloor
-\end{equation}
-
-So, being $\textrm{N}$ the number of products in the batch, we will have $\textrm{N}+1$ inequalities that limit the value of $T''$ by constants and again $T''$ will be defined by the smallest value.
-
-So, the analytical method can be decomposed into 4 steps:
+So, the analytical method for finding maximum $T$ can be decomposed into 4 steps:
 

### 2023-08-22 manuscript.tex
updating paper
explaining better exact method

@@
 
-\noindent Assim, $T$ pode ser calculado conforme equação em (\ref{eq:s17}):
-
-\begin{equation}
-\label{eq:s17}
- T = \min\{Z, \lfloor \min_i\{{\textrm{UD}_i / \textrm{p}_i}\} + \min\{ \min_i\{ (\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\}, (\textrm{O} + \textrm{I} + \sum_i S_i) / \sum_i \textrm{p}_i \}\rfloor\}
-\end{equation}
-
 So, the analytical method for finding maximum $T$ can be decomposed into 4 steps:
@@
 \begin{equation}
-T = T' + T''
+T^* = T' + T''
 \end{equation}
 \begin{equation}
-T = \min \{T , \textrm{Z}\}
+T = \min \{T^* , \textrm{Z}\}
 \end{equation}
 
-Note that there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
+Note that, à medida em que reduzimos o valor de $T'$, a consequente redução do valor de $D_{i}^{'}$ será atribuída diretamente à sobra $S_i$ e, portanto, there will be no change in the optimal solution if it is considered to $T'$, a value between 0 and the value found in step 1.
 Thus it is possible to use a simplification of the method presented, making $T' = 0$.
@@
 
-It is probably possible to extend this thinking to the solution of a class of linear optimization problems. However, we will work on this concept in an upcoming paper.
+Essa simplificação do método demonstra que o valor ótimo calculado para $T$ não depende da forma como a produção do produto $i$, $P_i$, é distribuída entre atendimento à demanda, $D_i$, outlets, $O_i$, e estoque de fábrica $I_i$.
 
-After determining a solution, the values of $D_i$, $O_i$ and $I_i$, $\forall i$, can be found by taking a solution from the undetermined system of inequalities:
-
-\begin{equation}
-D_i + O_i + I_i = p_i*T \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i \leq \textrm{UD}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-O_i \leq \textrm{UO}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{eq:resO}
-\sum_i{O_i} \leq \textrm{O}
-\end{equation}
-
-\begin{equation}
-I_i \leq \textrm{UI}_i \quad \forall i
-\end{equation}
-
-\begin{equation}
-\label{eq:resI}
-\sum_i{I_i} \leq \textrm{I}
-\end{equation}
-
-\begin{equation}
-\min \{\textrm{UD}_i - D_i, O_i + I_i\} = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-\min\{\textrm{O} - \sum_i\{ O_i\}, \textrm{UO}_i - O_i, I_i\} = 0 \quad \forall i
-\end{equation}
-
-\begin{equation}
-D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
-\end{equation}
-
-We can solve this system and determine the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by defining the priorities for distribution.
-The following three algorithms can be used to find a complete solution.
+We can determine now the values of $D_i$, $O_i$ and $I_i$, $\forall i$, simply by seguindo the priorities for distribution. The following three algorithms can be used to find a complete solution.
 
@@
 Then an initial production distribution can be done by the algorithm (\ref{alg:part02}).
+Esta distribuição é feita sem levar em consideração as restrições definidas para o conjunto de produtos do lote.
+$SO$ e $SI$ representam, respectivamente, o quantidade total disponível a ser enviada para os outlets e a quantidade total disponível para estoque em fábrica após a distribuição inicial.
+Caso esse valores sejam negativo, isso indica que a distribuição inicial proposta não é uma distribuição viável.
 
 \begin{algorithm}
-\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions in (\ref{eq:resO}) and (\ref{eq:resI}).}\label{alg:part02}
+\caption{Solving MBPTM problem | Part 02 - calculate $D_i$, $O_i$ and $I_i$, $\forall i$, ignoring the restrictions for the set of products of the batch.}\label{alg:part02}
 \begin{algorithmic}
@@
 
-After applying algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
+Assim, after applying algorithm (\ref{alg:part02}), if $SO \geq 0$ and $SI \geq 0$, solution found is an optimal solution.
 However, if $SO < 0$ or $SI <0$, solution is not yet feasible.
 But as the solution found to $T$ is feasible to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}), we have the following statements:
-
-\begin{lemma}
-Let \(T\) be a optimal solution to the problem defined in (\ref{MBPTMP01}) to (\ref{MBPTMP10}) and $SO$ and $SI$ defined by algorithm (\ref{alg:part02}), so: \\
 
@@
 
-\end{lemma}
-
-Therefore it is possible to meet the restrictions in (\ref{eq:resO}) and (\ref{eq:resI}) by applying the agorithm (\ref{alg:part03}).
+Therefore it is possible to meet the restrictions by applying the agorithm (\ref{alg:part03}).
+Neste algoritmo redistribuimos a produção do estoque para os outlets ou vice versa, respectivamente, em função de termos um $SI$ ou $SO$ negativo.
 
